---
title: "Tables and Figures"
format: docx
execute: 
  echo: false
  warning: false
---

```{r}
library(dplyr) #For general data manipulation
library(stringr) #For string manipulation
library(tidyr) #For pivoting
library(purrr)
library(flextable) # For Creating Tables
library(ggplot2)
full_experiment_dat <- read.csv("Clean_Data/experimental_data.csv")

full_experiment_dat <- full_experiment_dat |> 
  mutate(analytical_partial_cluster_edit = case_when(study_id %in% c("111568461","111565034","111576601","111565413","111565408") ~ "Ignored",
  study_id %in% c("111570022") ~ "Other,Random Effects,Ignored", .default = analytical_partial_cluster)) #These studies only have one partial cluster so coded them as ignored

long_cond <- read.csv("Clean_Data/treatment_condition_data.csv")
add_to_cond <- full_experiment_dat |> 
  select(citation_id, study_id, response_id, experiment, exp_level_random, exp_random_procedure, partial_nest, partial_class, pub_journal, partial_standardization, partial_diversity, partial_standardization_diversity_source, partial_assign_type, partial_size)

long_cond <- long_cond |> 
  left_join(add_to_cond, by = join_by(citation_id, study_id, response_id, experiment))

```

```{r}
## Sample size cleaning for across conditions
# long_cond |> 
#   filter(is.na(suppressWarnings(as.numeric(cond_exp_units_count)))) |> 
#   View()

long_cond <- long_cond |> 
  mutate(cond_exp_units_count_edit = case_when(str_detect(cond_exp_units_count, "\\*") ~ "Not Baseline",
                                               study_id %in% c("111573517", "111565447") ~ "Not Reported", #this study did not report their sample size
                                               study_id %in% c("111576847") & cond_name == "Standard Counseling" ~ "50", #Only the randomized part of the data
                                               is.na(suppressWarnings(as.numeric(cond_exp_units_count))) ~ "Not Reported",
                                               .default = cond_exp_units_count)) 

# long_cond |> 
#   filter(exp_level_random == "Cluster") |> 
#   filter(is.na(suppressWarnings(as.numeric(cond_obs_units_count)))) |> 
#   View()

long_cond <- long_cond |> 
  mutate(cond_obs_units_count_edit = case_when(exp_level_random == "Cluster" & study_id == "111565465" ~ str_remove(cond_obs_units_count, "\\*"), 
                                               exp_level_random == "Cluster" & study_id == "111571561" ~ "Not Baseline",
                                               exp_level_random == "Cluster" & study_id == "111571507" ~ "Not Reported",
                                               exp_level_random == "Cluster" & is.na(suppressWarnings(as.numeric(cond_obs_units_count))) ~ "Multiple Types of Observation Units",
                                               .default = cond_obs_units_count))
long_cond_sample_size <- long_cond |> 
  mutate(cond_obs_units_count_edit_num = suppressWarnings(as.numeric(cond_obs_units_count_edit)),
         cond_exp_units_count_edit_num = suppressWarnings(as.numeric(cond_exp_units_count_edit))) |> 
  ungroup()
```


## Article Characteristics 
* Year of publication
* Types of Randomization procedure
* Number of Experimental Conditions
* Number of primary or secondary analysis
* Sample size
```{r}
calc_freq <- function(experimental_dat, variable){
var_label <- deparse(substitute(variable))
full_experiment_dat |> 
  group_by({{variable}}) |> 
  summarise(count = n()) |> 
  rename(variable = {{variable}}) |> 
  mutate(across(everything(), as.character)) |> 
  bind_rows(data.frame(variable = var_label, count = NA)) |> 
  arrange(!is.na(count))
}


exp_characteristics <- bind_rows(calc_freq(full_experiment_dat, pub_year),
            calc_freq(full_experiment_dat, exp_level_random),
            calc_freq(full_experiment_dat, exp_random_procedure),
            calc_freq(full_experiment_dat, pub_primary_secondary))
exp_characteristics <- exp_characteristics |> 
  mutate(variable = case_when(variable == "pub_year" ~ "Publication Year",
                       variable == "exp_level_random" ~ "Unit of Randomization",
                       variable == "exp_random_procedure" ~ "Randomization Procedure",
                       variable == "pub_primary_secondary" ~ "Source",
                       .default = variable)) |> 
  rename(Characteristic =variable, `Number of Experiments` = count)

exp_characteristics |> 
  flextable() |> 
  padding(i = ~ !(Characteristic %in% c("Publication Year", "Unit of Randomization", "Randomization Procedure", "Source")), j = "Characteristic", padding.left = 20)|> 
  autofit() |> 
  font(font = "Times New Roman", part = "all") |> 
  border_remove() |> 
  hline_bottom(part = "body") |> 
  hline_top(part = "body") |> 
  hline_top(part = "header")

```

Sample size per randomized condition:
```{r}
# cluster randomized
cluster_sample_size_info <- long_cond_sample_size |> 
  filter(exp_level_random == "Cluster") |> 
  select(study_id, experiment, cond_type, cond_exp_units_count_edit, cond_exp_units_count_edit_num, cond_obs_units_count_edit, cond_obs_units_count_edit_num) |>
  mutate(cond_exp_units_count_edit = ifelse(!is.na(cond_exp_units_count_edit_num), "Reported Baseline", cond_exp_units_count_edit),
         cond_obs_units_count_edit = ifelse(!is.na(cond_obs_units_count_edit_num), "Reported Baseline", cond_obs_units_count_edit))
cluster_sample_size_stat <- cluster_sample_size_info |> 
  summarise(across(.cols = c(cond_exp_units_count_edit_num, cond_obs_units_count_edit_num), 
                   .fns = list(min =~min(.x, na.rm = TRUE),
                               q25 = ~quantile(.x, probs = .25, na.rm = TRUE), 
                               mean = ~mean(.x, na.rm = TRUE),
                               med = ~median(.x, na.rm = TRUE),
                               q75 = ~quantile(.x, probs = .75, na.rm = TRUE), 
                               max=~max(.x, na.rm = TRUE)))) |> 
 pivot_longer(cols = everything(), names_to = c("unit_type", ".value"), names_pattern = "cond_(exp|obs)_units_count_edit_num_(.*)")

exp_report_size <- cluster_sample_size_info |> 
  group_by(cond_exp_units_count_edit) |> 
  summarise(count = n_distinct(study_id, experiment)) |> 
  pivot_wider(names_from = cond_exp_units_count_edit, values_from = count) |> 
  mutate(unit_type = "exp")

obs_report_size <- cluster_sample_size_info |> 
  group_by(cond_obs_units_count_edit) |> 
  summarise(count = n_distinct(study_id, experiment)) |> 
  pivot_wider(names_from = cond_obs_units_count_edit, values_from = count) |> 
  mutate(unit_type = "obs")

report_size <- bind_rows(obs_report_size, exp_report_size) |> 
  replace_na(list(`Multiple Types of Observation Units` = 0))

cluster_sample_size_stat <- cluster_sample_size_stat |> 
  left_join(report_size) |> 
  mutate(unit_type = case_when(unit_type == "exp" ~ "Experimental",
                               unit_type == "obs" ~ "Observational")) |> 
  mutate(`Total Experiments` = `Reported Baseline` + `Not Reported` + `Not Baseline` + `Multiple Types of Observation Units`)

# Individual Units 
individual_sample_size_info <- long_cond_sample_size |> 
  filter(exp_level_random == "Individual") |> 
  select(study_id, experiment, cond_type, cond_exp_units_count_edit, cond_exp_units_count_edit_num) |>
  mutate(cond_exp_units_count_edit = ifelse(!is.na(cond_exp_units_count_edit_num), "Reported Baseline", cond_exp_units_count_edit))
individual_sample_size_stat <- individual_sample_size_info |> 
  summarise(across(.cols = c(cond_exp_units_count_edit_num), 
                   .fns = list(min =~min(.x, na.rm = TRUE),
                               q25 = ~quantile(.x, probs = .25, na.rm = TRUE), 
                               mean = ~mean(.x, na.rm = TRUE),
                               med = ~median(.x, na.rm = TRUE),
                               q75 = ~quantile(.x, probs = .75, na.rm = TRUE), 
                               max=~max(.x, na.rm = TRUE)))) |> 
 pivot_longer(cols = everything(), names_to = c("unit_type", ".value"), names_pattern = "cond_(exp)_units_count_edit_num_(.*)")

exp_report_size <- individual_sample_size_info |> 
  group_by(cond_exp_units_count_edit) |> 
  summarise(count = n_distinct(study_id, experiment)) |> 
  pivot_wider(names_from = cond_exp_units_count_edit, values_from = count) |> 
  mutate(unit_type = "exp")

individual_sample_size_stat <- individual_sample_size_stat |> 
  left_join(exp_report_size) |> 
  mutate(unit_type = case_when(unit_type == "exp" ~ "Experimental",
                               unit_type == "obs" ~ "Observational")) |> 
  mutate(`Total Experiments` = `Reported Baseline` + `Not Reported` + `Not Baseline`)

## Formating  -----

individual_format <- individual_sample_size_stat |> 
  select(-`Not Baseline`, -`Not Reported`) |> # 5 studies that have multiple type of observational units
  mutate(`Unit of Randomization` = "Individual") |> 
  relocate(`Unit of Randomization`, unit_type, `Reported Baseline`, `Total Experiments`) |> 
  rename(`Type of Unit` = unit_type, Min = min, `25th Quartile` = q25, Mean = mean, Median = med, `75th Quartile` = q75, Max = max)



cluster_format <- cluster_sample_size_stat |> 
  select(-`Not Baseline`, -`Not Reported`, -`Multiple Types of Observation Units`) |> 
  mutate(`Unit of Randomization` = "Cluster") |> 
  relocate(`Unit of Randomization`, unit_type, `Reported Baseline`, `Total Experiments`) |> 
  rename(`Type of Unit` = unit_type, Min = min, `25th Quartile` = q25, Mean = mean, Median = med, `75th Quartile` = q75, Max = max)

bind_rows(individual_format, cluster_format) |> 
  flextable() |> 
  colformat_double(digits = 1) |> 
  autofit() |> 
  font(font = "Times New Roman", part = "all") |> 
  border_remove() |> 
  hline_bottom(part = "body") |> 
  hline_top(part = "body") |> 
  hline_top(part = "header")
```


## Research Question 1 
1.	How prevalent are partial nested designs among randomized experiments in education and public health research?

```{r}
count_articles <- function(experimental_dat, ...){
    #... is the grouping variable for journal type or specific publication journal 
experimental_dat |> 
  group_by(exp_level_random, partial_nest,...) |> 
  summarise(count= n()) |> 
  mutate(experiment_type = paste(exp_level_random, partial_nest, sep = "_")) |> 
  pivot_wider(id_cols = c(...), names_from = experiment_type, values_from = count) |> 
  mutate(across(everything(), ~ifelse(is.na(.x), 0, .x)))
}
counts_publication  <- count_articles(full_experiment_dat, journal_type, pub_journal)
counts_journal_type <- count_articles(full_experiment_dat, journal_type) |> 
  mutate(pub_journal = journal_type)
counts_marginal <- count_articles(full_experiment_dat) |> 
  mutate(pub_journal = "Overall", journal_type = "Overall") 
stopifnot(!("Mix_Non-PN" %in% names(counts_publication))) #If this fails then remove line of code that adds this column in

number_exp_dat <- bind_rows(counts_publication, counts_journal_type, counts_marginal) |> 
  ungroup() |> 
  mutate(`Mix_Non-PN` = 0) |> ## Remove this line if Mix_Non-PN are found 
  rowwise() |> 
  mutate(Cluster_Total = sum(c_across(starts_with("Cluster"))),
         Individual_Total = sum(c_across(starts_with("Individual"))),
         Mix_Total = sum(c_across(starts_with("Mix"))),
         `All Designs_Total` = sum(c_across(ends_with("Total"))),
         `All Designs_PN` = sum(c_across(ends_with("_PN")))) |> 
  ungroup()

number_exp_dat |> 
  arrange( desc(journal_type), desc( `All Designs_Total`)) |> 
  select(-journal_type, pub_journal, -contains("Non-PN")) |> 
  relocate(pub_journal, starts_with("Individual"),starts_with("Cluster"), starts_with("Mix"), `All Designs_PN`, `All Designs_Total`) |> 
  rename(Publication = pub_journal) |> 
  flextable() |> 
  separate_header() |> 
  align(align = "center", part = "header") |>
  padding(i = ~ !(Publication %in% c("Overall", "Health", "Education")), j = "Publication", padding.left = 20) |> 
  add_header_row(values = c("","Level of Randomization", ""),
  colwidths = c(1,6, 2)) |> 
  autofit() |> 
  font(font = "Times New Roman", part = "all") |> 
  border_remove() |> 
  hline_bottom(part = "body") |> 
  hline_top(part = "body") |> 
  hline_top(part = "header")
```


```{r}
# long_cond |> 
#   relocate(study_id, pub_journal, partial_class) |> 
#   dataviewR::dataviewer()
# dataviewR::stop_all_dataviewers()
# ```
```

```{r}
# full_experiment_dat |> 
#   relocate(study_id, pub_journal, partial_class) |> 
#   dataviewR::dataviewer()
```

## Research Question 2
2.	What are the prevailing characteristics of partially nested designs, specifically regarding grouping structures, cluster assignment mechanisms, and sample size distributions?

Location of Partial Nesting:
```{r}
location_pn_dat <- full_experiment_dat |> 
  filter(partial_nest == "PN") |> 
  mutate(exp_TP = exp_treatment_provider_percent > 0 & exp_treatment_provider_percent < 1,
         exp_group = exp_treatment_group_percent > 0 & exp_treatment_group_percent < 1, 
         obs_TP = obs_treatment_provider_percent > 0 & obs_treatment_provider_percent < 1,
         obs_group = obs_treatment_group_percent > 0 & obs_treatment_group_percent < 1) |> 
  mutate(partial_class = case_when(
          study_id == "111571561" ~ "Complex", #Teachers had coaches and  professional course in different treatment conditons that gets comlapsed 
          study_id == "111568439" ~ "Complex", #coaches and group intervention across different treatment conditions 
          study_id == "111568554" ~ "Complex", #One treatment conditon had treatment providers one had group training class.
          exp_level_random == "Mix" ~ "Other",
          exp_group  ~ "Grouped",
         !exp_group & exp_TP ~ "Treatment Provider",
         !exp_group & !exp_TP & obs_group ~ "Observational Grouped",
         !exp_group & !exp_TP & !obs_group & obs_TP ~ "Observational Treatment Provider",
         .default = "Complex"))


new_partial_classes <- location_pn_dat |> 
  select(study_id, experiment, partial_class)

long_cond_sample_size <- long_cond_sample_size |> #replacing old partial classes
  select(-partial_class) |> 
  left_join(new_partial_classes)
```

```{r}
location_pn_dat_stat <- location_pn_dat |> 
  group_by(exp_level_random,partial_class, exp_TP, exp_group, obs_TP, obs_group) |> 
  summarise(Count = n()) |> 
  ungroup() 


  location_pn_dat_stat |> 
  mutate(across(c(-exp_level_random, -partial_class, -Count), .fns = ~ifelse(.x == FALSE, NA, "x"))) |> 
  relocate(exp_level_random,partial_class, exp_group, exp_TP, obs_group, obs_TP, Count) |> 
  arrange(exp_level_random,exp_group, exp_TP, obs_group, obs_TP) |> 
  rename(`Unit of Randomization` = exp_level_random, 
         `Type of Partial Nesting` = partial_class,
         `Experimental Unit_Treatment Provider Present` = exp_TP,
         `Experimental Unit_Group Setting Present` = exp_group,
         `Observational Unit_Treatment Provider Present` = obs_TP,
         `Observational Unit_Group Setting Present` = obs_group,
         `Number of Experiments` = Count) |> 
  flextable() |> 
  separate_header() |>
  autofit() |> 
  font(font = "Times New Roman", part = "all") |> 
  border_remove() |> 
  hline_bottom(part = "body") |> 
  hline_top(part = "body") |> 
  hline_top(part = "header")
```

Grouping Structures of Partial Nesting
```{r}
group_structures_stat <- location_pn_dat |> 
  group_by(exp_level_random, partial_class) |> 
  summarise(number_of_experiments = n()) |> 
  pivot_wider(id_cols = c(partial_class), 
  names_from =  c(exp_level_random),
  values_from = number_of_experiments) |> 
  mutate(across(everything(), ~replace_na(.x, 0))) |> 
  mutate(Total = Cluster + Individual + Mix) |> 
  ungroup()


overall_group_structures_stat <- group_structures_stat |> 
  summarise(across(c(-partial_class), sum)) |> 
  mutate(partial_class = "Overall")

group_structures_stat |> 
  bind_rows(overall_group_structures_stat) |> 
  arrange(desc(Total)) |> 
  relocate(partial_class, Total, Cluster, Individual, Mix) |> 
  rename(`Partial Nesting Classification` = partial_class) |> 
  flextable() |> 
  separate_header() |>
  padding(i = ~ !(`Partial Nesting Classification` %in% c("Overall")), j = "Partial Nesting Classification", padding.left = 20) |> 
  add_header_row(values = c("","Level of Randomization"), colwidths = c(2,3)) |> 
  align(align = "center", part = "header") |>
  autofit() |> 
  font(font = "Times New Roman", part = "all") |> 
  border_remove() |> 
  hline_bottom(part = "body") |> 
  hline_top(part = "body") |> 
  hline_top(part = "header")
```

Cluster Assignment Mechanism:

```{r}
cluster_assignment_stat <- location_pn_dat |> 
  group_by(partial_class, partial_assign_type) |> 
  summarise(number_of_experiments = n()) |> 
  pivot_wider(id_cols = c(partial_assign_type), 
  names_from =  c(partial_class),
  values_from = number_of_experiments) |> 
  mutate(across(everything(), ~replace_na(.x, 0))) |> 
  mutate(Total = rowSums(across(-partial_assign_type))) |> 
  ungroup()

overall_cluster_assignment_stat <- cluster_assignment_stat |> 
  summarise(across(c(-partial_assign_type), sum)) |> 
  mutate(partial_assign_type = "Overall")

cluster_assignment_stat |> 
  bind_rows(overall_cluster_assignment_stat) |> 
  arrange(desc(Total)) |> 
  relocate(partial_assign_type, Total, `Treatment Provider`, Grouped, `Observational Grouped`, `Observational Treatment Provider`, Complex, Other) |> 
  rename(`Cluster Assignment Type` = partial_assign_type) |> 
  flextable() |> 
  separate_header() |>
  padding(i = ~ !(`Cluster Assignment Type` %in% c("Overall")), j = "Cluster Assignment Type", padding.left = 20) |> 
  add_header_row(values = c("","Partial Nesting Classification"), colwidths = c(2,6)) |> 
  align(align = "center", part = "header") |>
  autofit() |> 
  font(font = "Times New Roman", part = "all") |> 
  border_remove() |> 
  hline_bottom(part = "body") |> 
  hline_top(part = "body") |> 
  hline_top(part = "header") |> 
  hline(i = 1, j = 3:8, part = "header")
```

```{r}
location_pn_dat |>  #Number of studies that did not describe how cluster's were formed
  filter(partial_assign_type == "Natural (Non-Random)") |> 
  summarise(sum(str_detect(string = toupper(partial_assign_detail), "^NOT|^NOR|UNCLEAR"), na.rm = TRUE))
```

Reporting of Partial clusters size:
```{r}
table(location_pn_dat$partial_size)
table(location_pn_dat$partial_size, location_pn_dat$partial_class)
```

Reporting number of partial clusters

```{r}
long_cond_report_num_PC <- long_cond_sample_size |> 
  filter(partial_nest == "PN") |> 
  filter(!is.na(cond_treatment_provider_num) | !is.na(cond_treatment_groups_num) ) |>#Removes treatment conditions that do not have any treatment nesting
  mutate(partial_cluster_report_num = case_when( #Indicator if any information is given around the number of partial clusters
  str_detect(toupper(cond_treatment_groups_num), "^NOT|^NOR|UNCLEAR") & str_detect(toupper(cond_treatment_provider_num), "^NOT|^NOR|UNCLEAR") ~ FALSE,
  partial_class == "Treatment Provider" ~  !str_detect(toupper(cond_treatment_provider_num), "^NOT|^NOR|UNCLEAR"),
  partial_class == "Grouped" ~ !str_detect(toupper(cond_treatment_groups_num), "^NOT|^NOR|UNCLEAR"),
  partial_class == "Observational Treatment Provider" ~ !str_detect(toupper(cond_treatment_provider_num), "^NOT|^NOR|UNCLEAR"),
  partial_class == "Observational Grouped" ~ !str_detect(toupper(cond_treatment_groups_num), "^NOT|^NOR|UNCLEAR"),
  partial_class == "Complex" ~ ifelse(partial_size == "Yes", TRUE, NA), #If size is not reported need to judge if number of partial clusters is reported
  partial_class == "Other" ~ ifelse(partial_size == "Yes", TRUE, NA))) |> #If size is not reported need to judge if number of partial clusters is reported
  mutate(partial_cluster_report_num = case_when( #manually fixing those that have NA 
    study_id == "111571616" ~ FALSE, #Individual Programming vs Pair programming with three combinations of pairs
    study_id == "111565397" ~ TRUE, #this experiment reported the number of group settings
    study_id == "111570010" ~ FALSE, #Does not report number of treatment provider or size
    .default = partial_cluster_report_num
  ))
partial_nest_report_num_dat <- long_cond_report_num_PC |> 
  group_by(study_id, experiment) |> 
  summarise(exp_report_info = sum(partial_cluster_report_num) >= 1)

table(partial_nest_report_num_dat$exp_report_info)

```

Sample Size of partial clusters:
```{r}
explore_samplesize <- long_cond_sample_size |> 
  filter(partial_nest == "PN", partial_class != "Complex",  partial_class != "Other") |> 
  mutate(partial_cluster_sample_size = case_when(
  partial_class == "Treatment Provider" ~ cond_treatment_provider_num,
  partial_class == "Grouped" ~ cond_treatment_groups_num,
  partial_class == "Observational Treatment Provider" ~ cond_treatment_provider_num,
  partial_class == "Observational Grouped" ~ cond_treatment_groups_num)) |> 
  mutate(relevant_unit_size = case_when( 
  study_id == "111565404"  ~ 100, #100 students are placed into teams
  study_id == "111565472" ~ 1835, #1836 math students nested within 70 math teachers whom did 58 group settings 
  partial_class == "Treatment Provider" ~ cond_exp_units_count_edit_num,
  partial_class == "Grouped" ~ cond_exp_units_count_edit_num,
  partial_class == "Observational Treatment Provider" ~ cond_obs_units_count_edit_num,
  partial_class == "Observational Grouped" ~ cond_obs_units_count_edit_num)) |> 
  filter(!is.na(partial_cluster_sample_size)) |> #Removes treatment conditions that did not have partial nesting
  mutate(partial_cluster_sample_size = case_when(  
    study_id == 111566857 ~ "Unclear", #This study did involve tutors in a group setting but unclear if students were always in the same group
    study_id == 111571616 ~ "Unclear", #Random pairs throughout the semester))
    .default = partial_cluster_sample_size)) |> 
  mutate(partial_cluster_sample_size =case_when(
    study_id == 111568543 ~ "9*", #Total number of coaches across all conditions since 6 are shared and 3 are unique to their condition
    .default = partial_cluster_sample_size)) |> 
  rowwise() |> 
  mutate(partial_cluster_sample_size_edit = 
      case_when(
        str_detect(partial_cluster_sample_size, "\\*") ~ str_remove(partial_cluster_sample_size, "\\*"), #remove *
        str_detect(partial_cluster_sample_size, "-") ~ as.character(round(mean(suppressWarnings(as.numeric(unlist(str_split(partial_cluster_sample_size, "-"))))))), #Find the mid point
        study_id == 111573573 ~ "6", #The max number of groups
        study_id == 111577860 ~ "9", #The Min number of treatment providers
        study_id == 111567874 ~ "18", #Max number of groups
      .default = partial_cluster_sample_size))

explore_samplesize <- explore_samplesize |> 
  group_by(study_id, experiment) |> 
      mutate(relevant_unit_size_edit = case_when(
       str_detect(partial_cluster_sample_size, "\\*") ~ sum(relevant_unit_size),
       .default =  relevant_unit_size)) |> 
  ungroup()

```

```{r}
add_PC_sample_size_to_experiment <- explore_samplesize |> 
  select(citation_id, study_id, response_id, experiment, partial_cluster_sample_size, relevant_unit_size) |> 
  group_by(citation_id, study_id, response_id, experiment) |> 
  summarise(partial_cluster_sample_size= paste(partial_cluster_sample_size, collapse = ","),
         relevant_unit_size = paste(relevant_unit_size, collapse = ","))
  

location_pn_dat <- location_pn_dat |> 
  left_join(select(add_PC_sample_size_to_experiment, citation_id, study_id, response_id, experiment, partial_cluster_sample_size, relevant_unit_size))

nrow(distinct(location_pn_dat))
```

Trying to summarise across experiments
number of experiments that did not report the number of partial clusters or size of partial clusters to calculate the number. 
number it is unclear due to the particular design characteristics 
number of experiments with just 1 partial cluster. 

```{r}
pc_samplesize_types  <- explore_samplesize |> 
  group_by(exp_level_random, partial_class,study_id,  experiment) |> #Sums across treatment conditions so that each row is experiment
  summarise(studies_no_report = sum(str_detect(tolower(partial_cluster_sample_size_edit), "report")),
            studies_unclear = sum(str_detect(tolower(partial_cluster_sample_size_edit), "unclear")),
            studies_report_calculate = sum(str_detect(partial_cluster_sample_size_edit, "^\\d+(\\.\\d+)?$"))) |> 
  group_by(exp_level_random, partial_class) |>
  summarise(experiments_no_report = sum(studies_no_report != 0),
            experiments_unclear = sum(studies_unclear != 0),
            experiments_report = sum(studies_report_calculate != 0),
            experiments_total = n()) |> 
  ungroup()
pc_samplesize_types_stat <- pc_samplesize_types |> 
  summarise(across(starts_with("experiments"), sum)) |> 
  mutate(partial_class = "Total") |> 
  bind_rows(pc_samplesize_types)

```



For experiments that did report the number of partial clusters. For students that report both ratio of 
For each type of partial class mean, median, min, max, lower_quartile, upper_quartile




```{r}
pc_samplesize_exp <- explore_samplesize |> 
  mutate(partial_cluster_sample_size_edit_num = suppressWarnings(as.numeric(partial_cluster_sample_size_edit))) |> 
  mutate(unit_per_pc = relevant_unit_size_edit/partial_cluster_sample_size_edit_num) |> 
  group_by(exp_level_random, partial_class, study_id, experiment) |> 
  summarise(average_unit_pc = mean(unit_per_pc, na.rm = TRUE), #average across treatment conditions 
            mean_pc = mean(partial_cluster_sample_size_edit_num, na.rm = TRUE)) |> 
  mutate(average_unit_pc = ifelse(study_id == 111571690, 17.5, average_unit_pc), #This study the observational unit is students but groups were made with teachers so this reflects the number of teachers in the study reather then the number of students under their care
         mean_pc = ifelse(study_id == 111571690, 32, mean_pc))

units_per_pc_stat <- pc_samplesize_exp |> 
  group_by(exp_level_random, partial_class) |> 
  summarise(across(.cols = c(average_unit_pc), 
                   .fns = list(min =~min(.x, na.rm = TRUE),
                               q25 = ~quantile(.x, probs = .25, na.rm = TRUE), 
                               mean = ~mean(.x, na.rm = TRUE),
                               med = ~median(.x, na.rm = TRUE),
                               q75 = ~quantile(.x, probs = .75, na.rm = TRUE), 
                               max=~max(.x, na.rm = TRUE))),
                               number_experiments = sum(!is.na(average_unit_pc)))

total_pc_stat <- location_pn_dat |> 
  group_by(partial_class, exp_level_random) |> 
  summarise(total = n())
units_per_pc_stat <- units_per_pc_stat |> 
  left_join(total_pc_stat)
units_per_pc_stat |> 
  rename(`Number of Experiments_Reported Info` = number_experiments,
         `Number of Experiments_Total` = total,
         `Unit of Randomization` = exp_level_random,
         `Type of Partial Nesting` = partial_class, 
         Min = average_unit_pc_min, 
         `25th Quartile` = average_unit_pc_q25, 
         Mean = average_unit_pc_mean, 
         Median = average_unit_pc_med, 
         `75th Quartile` = average_unit_pc_q75, 
         Max = average_unit_pc_max) |> 
  flextable() |> 
  colformat_double() |> 
  separate_header() |> 
  autofit() |> 
  font(font = "Times New Roman", part = "all") |> 
  border_remove() |> 
  hline_bottom(part = "body") |> 
  hline_top(part = "body") |> 
  hline_top(part = "header")
```

Number of partial clusters 
```{r}
number_pc_per_experiment_stat <- pc_samplesize_exp |> 
  group_by(exp_level_random, partial_class) |> 
  summarise(across(.cols = c(mean_pc), 
                   .fns = list(min =~min(.x, na.rm = TRUE),
                               q25 = ~quantile(.x, probs = .25, na.rm = TRUE), 
                               mean = ~mean(.x, na.rm = TRUE),
                               med = ~median(.x, na.rm = TRUE),
                               q75 = ~quantile(.x, probs = .75, na.rm = TRUE), 
                               max=~max(.x, na.rm = TRUE))),
                               number_experiments = sum(!is.na(mean_pc)))

total_pc_stat <- location_pn_dat |> 
  group_by(partial_class, exp_level_random) |> 
  summarise(total = n())
number_pc_per_experiment_stat <- number_pc_per_experiment_stat |> 
  left_join(total_pc_stat)
number_pc_per_experiment_stat |> 
  rename(`Number of Experiments_Reported Info` = number_experiments,
         `Number of Experiments_Total` = total,
         `Unit of Randomization` = exp_level_random,
         `Type of Partial Nesting` = partial_class, 
         Min = mean_pc_min, 
         `25th Quartile` = mean_pc_q25, 
         Mean = mean_pc_mean, 
         Median = mean_pc_med, 
         `75th Quartile` = mean_pc_q75, 
         Max = mean_pc_max) |> 
  flextable() |> 
  colformat_double() |> 
  separate_header() |> 
  autofit() |> 
  font(font = "Times New Roman", part = "all") |> 
  border_remove() |> 
  hline_bottom(part = "body") |> 
  hline_top(part = "body") |> 
  hline_top(part = "header")
```


## Research Question 3
3.	To what extent and by what statistical methods do researchers account for partial nesting? Among studies that account for partial nesting, how frequently and in what ways are cluster assignment mechanisms addressed in the analysis?

Types of Partial nesting:

```{r}
type_partial_nesting_dat <- location_pn_dat |> 
  group_by(exp_level_random, partial_class, journal_type) |> 
  summarise(Total= n(),
            `Not Ignored` = sum(analytical_partial_cluster_edit != "Ignored")) |> 
  pivot_wider(id_cols = c(exp_level_random, partial_class),
              names_from = journal_type,
              values_from = c(Total, `Not Ignored`),
              names_glue = "{.value}_{journal_type}") |> 
  mutate(`Total_All` = Total_Education + Total_Health,
         `Not Ignored_All` = `Not Ignored_Education` + `Not Ignored_Health`) |> 
  ungroup()
type_partial_nesting_dat <- type_partial_nesting_dat |> 
  summarise(across(-c(partial_class, exp_level_random), sum)) |> 
  mutate(partial_class = "Overall") |> 
  bind_rows(type_partial_nesting_dat)

type_partial_nesting_dat |> 
  arrange(desc(`Total_All`)) |> 
  relocate(exp_level_random, partial_class, starts_with("Total"), starts_with("Not Ignored")) |> 
  rename(`PN Classification` = partial_class,
         `Level of Randomization` = exp_level_random) |> 
  flextable() |> 
  separate_header()|> 
  autofit() |> 
  font(font = "Times New Roman", part = "all") |> 
  border_remove() |> 
  hline_bottom(part = "body") |> 
  hline_top(part = "body") |> 
  hline_top(part = "header")

```


```{r}
cluster_assignment_table <- full_experiment_dat |> 
  filter(partial_nest == "PN") |> 
  group_by(partial_assign_type, journal_type) |> 
  summarise(`Total`= n(),
            `Not Ignored` = sum(analytical_partial_cluster != "Ignored")) |> 
  ungroup() |> 
  complete(partial_assign_type, journal_type, fill = list(`Total` = 0)) |> 
  pivot_wider(id_cols = partial_assign_type,
              names_from = journal_type,
              values_from = c(`Total`),
              names_glue = "{journal_type}") |> 
  mutate(Overall = Education + Health)
cluster_assignment_table |> 
  rename(`Cluster Assignment Mechanism`= partial_assign_type) |> 
  flextable() |> 
  separate_header()|> 
  autofit() |> 
  font(font = "Times New Roman", part = "all") |> 
  border_remove() |> 
  hline_bottom(part = "body") |> 
  hline_top(part = "body") |> 
  hline_top(part = "header")

```

```{r}
analytical_approach_dat <- full_experiment_dat |> 
  filter(partial_nest == "PN",) |> 
  group_by(analytical_partial_cluster_edit) |> 
  summarise(Total = n()) |> 
  rename(`Analytical Approach`= analytical_partial_cluster_edit)

analytical_approach_dat <- full_experiment_dat |> 
  filter(partial_nest == "PN",) |>
  summarise(Total = n()) |> 
  mutate(`Analytical Approach` = "Overall") |> 
  bind_rows(analytical_approach_dat)


analytical_approach_dat |> 
  arrange(desc(Total)) |> 
  relocate(`Analytical Approach`, Total) |> 
  flextable() |> 
  autofit() |> 
  font(font = "Times New Roman", part = "all") |> 
  border_remove() |> 
  hline_bottom(part = "body") |> 
  hline_top(part = "body") |> 
  hline_top(part = "header")

```



## Research Question 5
5.	What are possible reasons researchers might not account for partial nesting in their analyses?
```{r}
ignore_PN_standard <- full_experiment_dat |> 
  filter(partial_nest == "PN", analytical_partial_cluster_edit == "Ignored") |> 
  group_by(journal_type, partial_class) |> 
  summarise(`Total Ignore` = n(),
            `Mention Standardization` = sum(partial_standardization == "Yes", na.rm = TRUE), #Why is there NA need to fix
            `Mention Diversity` = sum(partial_diversity == "Yes")) |> 
  pivot_wider(id_cols = c(partial_class),names_from = journal_type, values_from = c(`Total Ignore`, `Mention Standardization`, `Mention Diversity`),
names_glue = "{journal_type}_{.value}") |> 
  relocate(partial_class, starts_with("Education"), starts_with("Health")) |> 
  rename(`PN Classification` = partial_class)

ignore_PN_standard <- ignore_PN_standard |> 
  summarise(across(-`PN Classification`, sum)) |> 
  mutate(`PN Classification` = "Overall") |> 
  bind_rows(ignore_PN_standard) |> 
  mutate(`Overall_Total Ignore`= `Education_Total Ignore` + `Health_Total Ignore`)


ignore_PN_standard |> 
  relocate(`PN Classification`) |> 
  flextable() |> 
  separate_header()|> 
  autofit() |> 
  font(font = "Times New Roman", part = "all") |> 
  border_remove() |> 
  hline_bottom(part = "body") |> 
  hline_top(part = "body") |> 
  hline_top(part = "header")
```


For those that do not ignore PN:
```{r}
not_ignore_PN_standard <- full_experiment_dat |> 
  filter(partial_nest == "PN", analytical_partial_cluster_edit != "Ignored") |> 
  group_by(journal_type, partial_class) |> 
  summarise(`Total Ignore` = n(),
            `Mention Standardization` = sum(partial_standardization == "Yes", na.rm = TRUE), #Why is there NA need to fix
            `Mention Diversity` = sum(partial_diversity == "Yes")) |> 
  pivot_wider(id_cols = c(partial_class),names_from = journal_type, values_from = c(`Total Ignore`, `Mention Standardization`, `Mention Diversity`),
names_glue = "{journal_type}_{.value}") |> 
  relocate(partial_class, starts_with("Education"), starts_with("Health")) |> 
  rename(`PN Classification` = partial_class) |> 
  mutate(across(everything(), ~ifelse(is.na(.x), 0, .x)))

not_ignore_PN_standard <- not_ignore_PN_standard |> 
  summarise(across(-`PN Classification`, ~sum(.x, na.rm = TRUE))) |> 
  mutate(`PN Classification` = "Overall") |> 
  bind_rows(not_ignore_PN_standard) |> 
  mutate(`Overall_Total Ignore`= `Education_Total Ignore` + `Health_Total Ignore`)


not_ignore_PN_standard |> 
  relocate(`PN Classification`) |> 
  flextable() |> 
  separate_header()|> 
  autofit() |> 
  font(font = "Times New Roman", part = "all") |> 
  border_remove() |> 
  hline_bottom(part = "body") |> 
  hline_top(part = "body") |> 
  hline_top(part = "header")
```