---
title: "Tables and Figures"
format: docx
execute: 
  echo: false
  warning: false
---

```{r}
library(dplyr) #For general data manipulation
library(stringr) #For string manipulation
library(tidyr) #For pivoting
library(purrr)
library(flextable) # For Creating Tables
full_experiment_dat <- read.csv("Clean_Data/experimental_data.csv")

full_experiment_dat <- full_experiment_dat |> 
  mutate(analytical_partial_cluster_edit = case_when(study_id %in% c("111568461","111565034","111576601","111565413","111565408") ~ "Ignored",
  study_id %in% c("111570022") ~ "Other,Random Effects,Ignored", .default = analytical_partial_cluster)) #These studies only have one partial cluster so coded them as ignored

long_cond <- read.csv("Clean_Data/treatment_condition_data.csv")
add_to_cond <- full_experiment_dat |> 
  select(citation_id, study_id, response_id, experiment, exp_level_random, exp_random_procedure, partial_nest, partial_class, pub_journal, partial_standardization, partial_diversity, partial_standardization_diversity_source)

long_cond <- long_cond |> 
  left_join(add_to_cond, by = join_by(citation_id, study_id, response_id, experiment))

```

```{r}
## Sample size cleaning for across conditions
# long_cond |> 
#   filter(is.na(suppressWarnings(as.numeric(cond_exp_units_count)))) |> 
#   View()

long_cond <- long_cond |> 
  mutate(cond_exp_units_count_edit = case_when(str_detect(cond_exp_units_count, "\\*") ~ "Not Baseline",
                                               study_id %in% c("111573517", "111565447") ~ "Not Reported", #this study did not report their sample size
                                               study_id %in% c("111576847") & cond_name == "Standard Counseling" ~ "50", #Only the randomized part of the data
                                               is.na(suppressWarnings(as.numeric(cond_exp_units_count))) ~ "Not Reported",
                                               .default = cond_exp_units_count)) 

# long_cond |> 
#   filter(exp_level_random == "Cluster") |> 
#   filter(is.na(suppressWarnings(as.numeric(cond_obs_units_count)))) |> 
#   View()

long_cond <- long_cond |> 
  mutate(cond_obs_units_count_edit = case_when(exp_level_random == "Cluster" & study_id == "111565465" ~ str_remove(cond_obs_units_count, "\\*"), 
                                               exp_level_random == "Cluster" & study_id == "111571561" ~ "Not Baseline",
                                               exp_level_random == "Cluster" & study_id == "111571507" ~ "Not Reported",
                                               exp_level_random == "Cluster" & is.na(suppressWarnings(as.numeric(cond_obs_units_count))) ~ "Multiple Types of Observation Units",
                                               .default = cond_obs_units_count))
long_cond_sample_size <- long_cond |> 
  mutate(cond_obs_units_count_edit_num = suppressWarnings(as.numeric(cond_obs_units_count_edit)),
         cond_exp_units_count_edit_num = suppressWarnings(as.numeric(cond_exp_units_count_edit))) |> 
  ungroup()
```


## Article Characteristics 
* Year of publication
* Types of Randomization procedure
* Number of Experimental Conditions
* Number of primary or secondary analysis
* Sample size
```{r}
calc_freq <- function(experimental_dat, variable){
var_label <- deparse(substitute(variable))
full_experiment_dat |> 
  group_by({{variable}}) |> 
  summarise(count = n()) |> 
  rename(variable = {{variable}}) |> 
  mutate(across(everything(), as.character)) |> 
  bind_rows(data.frame(variable = var_label, count = NA)) |> 
  arrange(!is.na(count))
}


exp_characteristics <- bind_rows(calc_freq(full_experiment_dat, pub_year),
            calc_freq(full_experiment_dat, exp_level_random),
            calc_freq(full_experiment_dat, exp_random_procedure),
            calc_freq(full_experiment_dat, pub_primary_secondary))
exp_characteristics <- exp_characteristics |> 
  mutate(variable = case_when(variable == "pub_year" ~ "Publication Year",
                       variable == "exp_level_random" ~ "Unit of Randomization",
                       variable == "exp_random_procedure" ~ "Randomization Procedure",
                       variable == "pub_primary_secondary" ~ "Source",
                       .default = variable)) |> 
  rename(Characteristic =variable, `Number of Experiments` = count)

exp_characteristics |> 
  flextable() |> 
  padding(i = ~ !(Characteristic %in% c("Publication Year", "Unit of Randomization", "Randomization Procedure", "Source")), j = "Characteristic", padding.left = 20)|> 
  autofit() |> 
  font(font = "Times New Roman", part = "all") |> 
  border_remove() |> 
  hline_bottom(part = "body") |> 
  hline_top(part = "body") |> 
  hline_top(part = "header")

```

Sample size per randomized condition:
```{r}
# cluster randomized
cluster_sample_size_info <- long_cond_sample_size |> 
  filter(exp_level_random == "Cluster") |> 
  select(study_id, experiment, cond_type, cond_exp_units_count_edit, cond_exp_units_count_edit_num, cond_obs_units_count_edit, cond_obs_units_count_edit_num) |>
  mutate(cond_exp_units_count_edit = ifelse(!is.na(cond_exp_units_count_edit_num), "Reported Baseline", cond_exp_units_count_edit),
         cond_obs_units_count_edit = ifelse(!is.na(cond_obs_units_count_edit_num), "Reported Baseline", cond_obs_units_count_edit))
cluster_sample_size_stat <- cluster_sample_size_info |> 
  summarise(across(.cols = c(cond_exp_units_count_edit_num, cond_obs_units_count_edit_num), 
                   .fns = list(min =~min(.x, na.rm = TRUE),
                               q25 = ~quantile(.x, probs = .25, na.rm = TRUE), 
                               mean = ~mean(.x, na.rm = TRUE),
                               med = ~median(.x, na.rm = TRUE),
                               q75 = ~quantile(.x, probs = .75, na.rm = TRUE), 
                               max=~max(.x, na.rm = TRUE)))) |> 
 pivot_longer(cols = everything(), names_to = c("unit_type", ".value"), names_pattern = "cond_(exp|obs)_units_count_edit_num_(.*)")

exp_report_size <- cluster_sample_size_info |> 
  group_by(cond_exp_units_count_edit) |> 
  summarise(count = n_distinct(study_id, experiment)) |> 
  pivot_wider(names_from = cond_exp_units_count_edit, values_from = count) |> 
  mutate(unit_type = "exp")

obs_report_size <- cluster_sample_size_info |> 
  group_by(cond_obs_units_count_edit) |> 
  summarise(count = n_distinct(study_id, experiment)) |> 
  pivot_wider(names_from = cond_obs_units_count_edit, values_from = count) |> 
  mutate(unit_type = "obs")

report_size <- bind_rows(obs_report_size, exp_report_size) |> 
  replace_na(list(`Multiple Types of Observation Units` = 0))

cluster_sample_size_stat <- cluster_sample_size_stat |> 
  left_join(report_size) |> 
  mutate(unit_type = case_when(unit_type == "exp" ~ "Experimental",
                               unit_type == "obs" ~ "Observational")) |> 
  mutate(`Total Experiments` = `Reported Baseline` + `Not Reported` + `Not Baseline` + `Multiple Types of Observation Units`)

# Individual Units 
individual_sample_size_info <- long_cond_sample_size |> 
  filter(exp_level_random == "Individual") |> 
  select(study_id, experiment, cond_type, cond_exp_units_count_edit, cond_exp_units_count_edit_num) |>
  mutate(cond_exp_units_count_edit = ifelse(!is.na(cond_exp_units_count_edit_num), "Reported Baseline", cond_exp_units_count_edit))
individual_sample_size_stat <- individual_sample_size_info |> 
  summarise(across(.cols = c(cond_exp_units_count_edit_num), 
                   .fns = list(min =~min(.x, na.rm = TRUE),
                               q25 = ~quantile(.x, probs = .25, na.rm = TRUE), 
                               mean = ~mean(.x, na.rm = TRUE),
                               med = ~median(.x, na.rm = TRUE),
                               q75 = ~quantile(.x, probs = .75, na.rm = TRUE), 
                               max=~max(.x, na.rm = TRUE)))) |> 
 pivot_longer(cols = everything(), names_to = c("unit_type", ".value"), names_pattern = "cond_(exp)_units_count_edit_num_(.*)")

exp_report_size <- individual_sample_size_info |> 
  group_by(cond_exp_units_count_edit) |> 
  summarise(count = n_distinct(study_id, experiment)) |> 
  pivot_wider(names_from = cond_exp_units_count_edit, values_from = count) |> 
  mutate(unit_type = "exp")

individual_sample_size_stat <- individual_sample_size_stat |> 
  left_join(exp_report_size) |> 
  mutate(unit_type = case_when(unit_type == "exp" ~ "Experimental",
                               unit_type == "obs" ~ "Observational")) |> 
  mutate(`Total Experiments` = `Reported Baseline` + `Not Reported` + `Not Baseline`)

## Formating  -----

individual_format <- individual_sample_size_stat |> 
  select(-`Not Baseline`, -`Not Reported`) |> # 5 studies that have multiple type of observational units
  mutate(`Unit of Randomization` = "Individual") |> 
  relocate(`Unit of Randomization`, unit_type, `Reported Baseline`, `Total Experiments`) |> 
  rename(`Type of Unit` = unit_type, Min = min, `25th Quartile` = q25, Mean = mean, Median = med, `75th Quartile` = q75, Max = max)



cluster_format <- cluster_sample_size_stat |> 
  select(-`Not Baseline`, -`Not Reported`, -`Multiple Types of Observation Units`) |> 
  mutate(`Unit of Randomization` = "Cluster") |> 
  relocate(`Unit of Randomization`, unit_type, `Reported Baseline`, `Total Experiments`) |> 
  rename(`Type of Unit` = unit_type, Min = min, `25th Quartile` = q25, Mean = mean, Median = med, `75th Quartile` = q75, Max = max)

bind_rows(individual_format, cluster_format) |> 
  flextable() |> 
  colformat_double(digits = 1) |> 
  autofit() |> 
  font(font = "Times New Roman", part = "all") |> 
  border_remove() |> 
  hline_bottom(part = "body") |> 
  hline_top(part = "body") |> 
  hline_top(part = "header")
```


## Research Question 1 
1.	How prevalent are partial nested designs among randomized experiments in education and public health research?

```{r}
count_articles <- function(experimental_dat, ...){
    #... is the grouping variable for journal type or specific publication journal 
experimental_dat |> 
  group_by(exp_level_random, partial_nest,...) |> 
  summarise(count= n()) |> 
  mutate(experiment_type = paste(exp_level_random, partial_nest, sep = "_")) |> 
  pivot_wider(id_cols = c(...), names_from = experiment_type, values_from = count) |> 
  mutate(across(everything(), ~ifelse(is.na(.x), 0, .x)))
}
counts_publication  <- count_articles(full_experiment_dat, journal_type, pub_journal)
counts_journal_type <- count_articles(full_experiment_dat, journal_type) |> 
  mutate(pub_journal = journal_type)
counts_marginal <- count_articles(full_experiment_dat) |> 
  mutate(pub_journal = "Overall", journal_type = "Overall") 
stopifnot(!("Mix_Non-PN" %in% names(counts_publication))) #If this fails then remove line of code that adds this column in

number_exp_dat <- bind_rows(counts_publication, counts_journal_type, counts_marginal) |> 
  ungroup() |> 
  mutate(`Mix_Non-PN` = 0) |> ## Remove this line if Mix_Non-PN are found 
  rowwise() |> 
  mutate(Cluster_Total = sum(c_across(starts_with("Cluster"))),
         Individual_Total = sum(c_across(starts_with("Individual"))),
         Mix_Total = sum(c_across(starts_with("Mix"))),
         `All Designs_Total` = sum(c_across(ends_with("Total"))),
         `All Designs_PN` = sum(c_across(ends_with("_PN")))) |> 
  ungroup()

number_exp_dat |> 
  arrange( desc(journal_type), desc( `All Designs_Total`)) |> 
  select(-journal_type, pub_journal, -contains("Non-PN")) |> 
  relocate(pub_journal, starts_with("Individual"),starts_with("Cluster"), starts_with("Mix"), `All Designs_PN`, `All Designs_Total`) |> 
  rename(Publication = pub_journal) |> 
  flextable() |> 
  separate_header() |> 
  align(align = "center", part = "header") |>
  padding(i = ~ !(Publication %in% c("Overall", "Health", "Education")), j = "Publication", padding.left = 20) |> 
  add_header_row(values = c("","Unit of Randomization", ""),
  colwidths = c(1,6, 2)) |> 
  autofit() |> 
  font(font = "Times New Roman", part = "all") |> 
  border_remove() |> 
  hline_bottom(part = "body") |> 
  hline_top(part = "body") |> 
  hline_top(part = "header")
```


```{r}
# long_cond |> 
#   relocate(study_id, pub_journal, partial_class) |> 
#   dataviewR::dataviewer()
# dataviewR::stop_all_dataviewers()
# ```
```

```{r}
# full_experiment_dat |> 
#   relocate(study_id, pub_journal, partial_class) |> 
#   dataviewR::dataviewer()
```

## Research Question 2
2.	What are the prevailing characteristics of partially nested designs, specifically regarding grouping structures, cluster assignment mechanisms, and sample size distributions?

Location of Partial Nesting:
```{r}
location_pn_dat <- full_experiment_dat |> 
  filter(partial_nest == "PN") |> 
  mutate(exp_TP = exp_treatment_provider_percent > 0 & exp_treatment_provider_percent < 1,
         exp_group = exp_treatment_group_percent > 0 & exp_treatment_group_percent < 1, 
         obs_TP = obs_treatment_provider_percent > 0 & obs_treatment_provider_percent < 1,
         obs_group = obs_treatment_group_percent > 0 & obs_treatment_group_percent < 1)

# weird <- location_pn_dat |> 
#   filter(exp_TP == FALSE, exp_group == FALSE, exp_level_random == "Individual") |> 
#   pull(study_id) 

# long_cond |>  # The multigroup PNRDs
#   filter(study_id %in% weird) |> 
#   View()

location_pn_dat_stat <- location_pn_dat |> 
  group_by(exp_level_random, exp_TP, exp_group, obs_TP, obs_group) |> 
  summarise(Count = n()) |> 
  ungroup() 

location_pn_dat_stat |> 
  mutate(across(-exp_level_random, .fns = ~ifelse(.x == FALSE, NA, .x))) |> 
  arrange(exp_level_random, desc(Count)) |> 
  rename(`Unit of Randomization` = exp_level_random, 
         `Experimental Unit_Treatment Provider Present` = exp_TP,
         `Experimental Unit_Group Setting Present` = exp_group,
         `Observational Unit_Treatment Provider Present` = obs_TP,
         `Observational Unit_Group Setting Present` = obs_group) |> 
  flextable() |> 
  separate_header() |>
  autofit() |> 
  font(font = "Times New Roman", part = "all") |> 
  border_remove() |> 
  hline_bottom(part = "body") |> 
  hline_top(part = "body") |> 
  hline_top(part = "header")
```

Sample Size of partial clusters:

```{r}
exp_treatment_groups_samplesize <- long_cond_sample_size |> 
  filter(partial_nest == "PN") |> 
  filter(cond_treatment_groups_exp == "Yes") |> 
  select(cond_exp_units_count_edit_num,  cond_treatment_groups_num)
```


Types of Partial nesting:

```{r}
type_partial_nesting_dat <- full_experiment_dat |> 
  filter(partial_nest == "PN") |> 
  group_by(partial_class, journal_type) |> 
  summarise(Total= n(),
            `Not Ignored` = sum(analytical_partial_cluster_edit != "Ignored")) |> 
  pivot_wider(id_cols = partial_class,
              names_from = journal_type,
              values_from = c(Total, `Not Ignored`),
              names_glue = "{.value}_{journal_type}") |> 
  mutate(`Total_All` = Total_Education + Total_Health,
         `Not Ignored_All` = `Not Ignored_Education` + `Not Ignored_Health`) |> 
  ungroup()
type_partial_nesting_dat <- type_partial_nesting_dat |> 
  summarise(across(-partial_class, sum)) |> 
  mutate(partial_class = "Overall") |> 
  bind_rows(type_partial_nesting_dat)

type_partial_nesting_dat |> 
  arrange(desc(`Total_All`)) |> 
  relocate(partial_class, starts_with("Total"), starts_with("Not Ignored")) |> 
  rename(`PN Classification` = partial_class) |> 
  flextable() |> 
  separate_header()|> 
  autofit() |> 
  font(font = "Times New Roman", part = "all") |> 
  border_remove() |> 
  hline_bottom(part = "body") |> 
  hline_top(part = "body") |> 
  hline_top(part = "header")

```

Cluster Assignment Mechanism:
```{r}
cluster_assignment_table <- full_experiment_dat |> 
  filter(partial_nest == "PN") |> 
  group_by(partial_assign_type, journal_type) |> 
  summarise(`Total`= n(),
            `Not Ignored` = sum(analytical_partial_cluster != "Ignored")) |> 
  ungroup() |> 
  complete(partial_assign_type, journal_type, fill = list(`Total` = 0)) |> 
  pivot_wider(id_cols = partial_assign_type,
              names_from = journal_type,
              values_from = c(`Total`),
              names_glue = "{journal_type}") |> 
  mutate(Overall = Education + Health)
cluster_assignment_table |> 
  rename(`Cluster Assignment Mechanism`= partial_assign_type) |> 
  flextable() |> 
  separate_header()|> 
  autofit() |> 
  font(font = "Times New Roman", part = "all") |> 
  border_remove() |> 
  hline_bottom(part = "body") |> 
  hline_top(part = "body") |> 
  hline_top(part = "header")

```

Cluster Size and Number:

Challenging data is really messy
```{r}
# long_cond |> 
#   filter(partial_nest == "PN") |> 
#   select(partial_class, cond_treatment_groups_num, cond_treatment_provider_num) |> 
#   View()
```


## Research Question 3
3.	To what extent and by what statistical methods do researchers account for partial nesting? Among studies that account for partial nesting, how frequently and in what ways are cluster assignment mechanisms addressed in the analysis?

```{r}
analytical_approach_dat <- full_experiment_dat |> 
  filter(partial_nest == "PN",) |> 
  group_by(analytical_partial_cluster_edit) |> 
  summarise(Total = n()) |> 
  rename(`Analytical Approach`= analytical_partial_cluster_edit)

analytical_approach_dat <- full_experiment_dat |> 
  filter(partial_nest == "PN",) |>
  summarise(Total = n()) |> 
  mutate(`Analytical Approach` = "Overall") |> 
  bind_rows(analytical_approach_dat)


analytical_approach_dat |> 
  arrange(desc(Total)) |> 
  relocate(`Analytical Approach`, Total) |> 
  flextable() |> 
  autofit() |> 
  font(font = "Times New Roman", part = "all") |> 
  border_remove() |> 
  hline_bottom(part = "body") |> 
  hline_top(part = "body") |> 
  hline_top(part = "header")

```



## Research Question 5
5.	What are possible reasons researchers might not account for partial nesting in their analyses?
```{r}
ignore_PN_standard <- full_experiment_dat |> 
  filter(partial_nest == "PN", analytical_partial_cluster_edit == "Ignored") |> 
  group_by(journal_type, partial_class) |> 
  summarise(`Total Ignore` = n(),
            `Mention Standardization` = sum(partial_standardization == "Yes", na.rm = TRUE), #Why is there NA need to fix
            `Mention Diversity` = sum(partial_diversity == "Yes")) |> 
  pivot_wider(id_cols = c(partial_class),names_from = journal_type, values_from = c(`Total Ignore`, `Mention Standardization`, `Mention Diversity`),
names_glue = "{journal_type}_{.value}") |> 
  relocate(partial_class, starts_with("Education"), starts_with("Health")) |> 
  rename(`PN Classification` = partial_class)

ignore_PN_standard <- ignore_PN_standard |> 
  summarise(across(-`PN Classification`, sum)) |> 
  mutate(`PN Classification` = "Overall") |> 
  bind_rows(ignore_PN_standard) |> 
  mutate(`Overall_Total Ignore`= `Education_Total Ignore` + `Health_Total Ignore`)


ignore_PN_standard |> 
  relocate(`PN Classification`) |> 
  flextable() |> 
  separate_header()|> 
  autofit() |> 
  font(font = "Times New Roman", part = "all") |> 
  border_remove() |> 
  hline_bottom(part = "body") |> 
  hline_top(part = "body") |> 
  hline_top(part = "header")
```


For those that do not ignore PN:
```{r}
not_ignore_PN_standard <- full_experiment_dat |> 
  filter(partial_nest == "PN", analytical_partial_cluster_edit != "Ignored") |> 
  group_by(journal_type, partial_class) |> 
  summarise(`Total Ignore` = n(),
            `Mention Standardization` = sum(partial_standardization == "Yes", na.rm = TRUE), #Why is there NA need to fix
            `Mention Diversity` = sum(partial_diversity == "Yes")) |> 
  pivot_wider(id_cols = c(partial_class),names_from = journal_type, values_from = c(`Total Ignore`, `Mention Standardization`, `Mention Diversity`),
names_glue = "{journal_type}_{.value}") |> 
  relocate(partial_class, starts_with("Education"), starts_with("Health")) |> 
  rename(`PN Classification` = partial_class) |> 
  mutate(across(everything(), ~ifelse(is.na(.x), 0, .x)))

not_ignore_PN_standard <- not_ignore_PN_standard |> 
  summarise(across(-`PN Classification`, ~sum(.x, na.rm = TRUE))) |> 
  mutate(`PN Classification` = "Overall") |> 
  bind_rows(not_ignore_PN_standard) |> 
  mutate(`Overall_Total Ignore`= `Education_Total Ignore` + `Health_Total Ignore`)


not_ignore_PN_standard |> 
  relocate(`PN Classification`) |> 
  flextable() |> 
  separate_header()|> 
  autofit() |> 
  font(font = "Times New Roman", part = "all") |> 
  border_remove() |> 
  hline_bottom(part = "body") |> 
  hline_top(part = "body") |> 
  hline_top(part = "header")
```