---
title: "Tables and Figures"
format: docx
execute: 
  echo: false
  warning: false
---

```{r}
library(dplyr) #For general data manipulation
library(stringr) #For string manipulation
library(tidyr) #For pivoting
library(purrr)
library(flextable) # For Creating Tables
full_experiment_dat <- read.csv("Clean_Data/experimental_data.csv")
long_cond <- read.csv("Clean_Data/treatment_condition_data.csv")
add_to_cond <- full_experiment_dat |> 
  select(citation_id, study_id, response_id, experiment, exp_level_random, exp_random_procedure, partial_nest)

long_cond <- long_cond |> 
  left_join(add_to_cond, by = join_by(citation_id, study_id, response_id, experiment))

```

```{r}
## Sample size cleaning for across conditions
# long_cond |> 
#   filter(is.na(suppressWarnings(as.numeric(cond_exp_units_count)))) |> 
#   View()

long_cond <- long_cond |> 
  mutate(cond_exp_units_count_edit = case_when(str_detect(cond_exp_units_count, "\\*") ~ "Not Baseline",
                                               study_id %in% c("111573517", "111565447") ~ "Not Reported", #this study did not report their sample size
                                               study_id %in% c("111576847") & cond_name == "Standard Counseling" ~ "50", #Only the randomized part of the data
                                               is.na(suppressWarnings(as.numeric(cond_exp_units_count))) ~ "Not Reported",
                                               .default = cond_exp_units_count)) 

# long_cond |> 
#   filter(exp_level_random == "Cluster") |> 
#   filter(is.na(suppressWarnings(as.numeric(cond_obs_units_count)))) |> 
#   View()

long_cond <- long_cond |> 
  mutate(cond_obs_units_count_edit = case_when(exp_level_random == "Cluster" & study_id == "111565465" ~ str_remove(cond_obs_units_count, "\\*"), 
                                               exp_level_random == "Cluster" & study_id == "111571561" ~ "Not Baseline",
                                               exp_level_random == "Cluster" & study_id == "111571507" ~ "Not Reported",
                                               exp_level_random == "Cluster" & is.na(suppressWarnings(as.numeric(cond_obs_units_count))) ~ "Multiple Types of Observation Units",
                                               .default = cond_obs_units_count))
long_cond_sample_size <- long_cond |> 
  filter(exp_level_random != "Mix") |> 
  mutate(cond_obs_units_count_edit_num = suppressWarnings(as.numeric(cond_obs_units_count_edit)),
         cond_exp_units_count_edit_num = suppressWarnings(as.numeric(cond_exp_units_count_edit))) |> 
  group_by(exp_level_random) |> 
  mutate(cond_exp_units_count_bin = case_when(!is.na(cond_exp_units_count_edit_num) ~ cut(cond_exp_units_count_edit_num, 
                                                                                                   breaks = quantile(cond_exp_units_count_edit_num, 
                                                                                                   na.rm = TRUE),
                                                                                                   include.lowest = TRUE),
                                                       .default = cond_exp_units_count_edit),
         cond_obs_units_count_bin = case_when(!is.na(cond_obs_units_count_edit_num) ~ cut(cond_obs_units_count_edit_num, 
                                                                                                   breaks = quantile(cond_obs_units_count_edit_num, 
                                                                                                   na.rm = TRUE),
                                                                                                   include.lowest = TRUE),
                                                       .default = cond_obs_units_count_edit))
# long_cond_sample_size |> 
#   group_by(exp_level_random, cond_type, cond_exp_units_count_bin) |>
#   summarise(count = n())
```

## Article Characteristics 
* Year of publication
* Types of Randomization procedure
* Number of Experimental Conditions
* Number of primary or secondary analysis
* Sample size (Challenging pin in for now)
```{r}
calc_freq <- function(experimental_dat, variable){
var_label <- deparse(substitute(variable))
full_experiment_dat |> 
  group_by({{variable}}) |> 
  summarise(count = n()) |> 
  rename(variable = {{variable}}) |> 
  mutate(across(everything(), as.character)) |> 
  bind_rows(data.frame(variable = var_label, count = NA)) |> 
  arrange(!is.na(count))
}


exp_characteristics <- bind_rows(calc_freq(full_experiment_dat, pub_year),
            calc_freq(full_experiment_dat, exp_level_random),
            calc_freq(full_experiment_dat, exp_random_procedure),
            calc_freq(full_experiment_dat, pub_primary_secondary))
exp_characteristics <- exp_characteristics |> 
  mutate(variable = case_when(variable == "pub_year" ~ "Publication Year",
                       variable == "exp_level_random" ~ "Unit of Randomization",
                       variable == "exp_random_procedure" ~ "Randomization Procedure",
                       variable == "pub_primary_secondary" ~ "Source",
                       .default = variable)) |> 
  rename(Characteristic =variable, `Number of Experiments` = count)

exp_characteristics |> 
  flextable() |> 
  padding(i = ~ !(Characteristic %in% c("Publication Year", "Unit of Randomization", "Randomization Procedure", "Source")), j = "Characteristic", padding.left = 20)|> 
  autofit() |> 
  font(font = "Times New Roman", part = "all") |> 
  border_remove() |> 
  hline_bottom(part = "body") |> 
  hline_top(part = "body") |> 
  hline_top(part = "header")

```


## Research Question 1 
1.	How prevalent are partial nested designs among randomized experiments in education and public health research?

```{r}
count_articles <- function(experimental_dat, ...){
    #... is the grouping variable for journal type or specific publication journal 
experimental_dat |> 
  group_by(exp_level_random, partial_nest,...) |> 
  summarise(count= n()) |> 
  mutate(experiment_type = paste(exp_level_random, partial_nest, sep = "_")) |> 
  pivot_wider(id_cols = c(...), names_from = experiment_type, values_from = count) |> 
  mutate(across(everything(), ~ifelse(is.na(.x), 0, .x)))
}
counts_publication  <- count_articles(full_experiment_dat, journal_type, pub_journal)
counts_journal_type <- count_articles(full_experiment_dat, journal_type) |> 
  mutate(pub_journal = journal_type)
counts_marginal <- count_articles(full_experiment_dat) |> 
  mutate(pub_journal = "Overall", journal_type = "Overall") 
stopifnot(!("Mix_Non-PN" %in% names(counts_publication))) #If this fails then remove line of code that adds this column in

number_exp_dat <- bind_rows(counts_publication, counts_journal_type, counts_marginal) |> 
  ungroup() |> 
  mutate(`Mix_Non-PN` = 0) |> ## Remove this line if Mix_Non-PN are found 
  rowwise() |> 
  mutate(Cluster_Total = sum(c_across(starts_with("Cluster"))),
         Individual_Total = sum(c_across(starts_with("Individual"))),
         Mix_Total = sum(c_across(starts_with("Mix"))),
         `All Designs_Total` = sum(c_across(ends_with("Total"))),
         `All Designs_PN` = sum(c_across(ends_with("_PN")))) |> 
  ungroup()

number_exp_dat |> 
  arrange( desc(journal_type), desc( `All Designs_Total`)) |> 
  select(-journal_type, pub_journal, -contains("Non-PN")) |> 
  relocate(pub_journal, starts_with("Individual"),starts_with("Cluster"), starts_with("Mix"), `All Designs_PN`, `All Designs_Total`) |> 
  rename(Publication = pub_journal) |> 
  flextable() |> 
  separate_header() |> 
  align(align = "center", part = "header") |>
  padding(i = ~ !(Publication %in% c("Overall", "Health", "Education")), j = "Publication", padding.left = 20) |> 
  add_header_row(values = c("","Unit of Randomization", ""),
  colwidths = c(1,6, 2)) |> 
  autofit() |> 
  font(font = "Times New Roman", part = "all") |> 
  border_remove() |> 
  hline_bottom(part = "body") |> 
  hline_top(part = "body") |> 
  hline_top(part = "header")
```


## Research Question 2
2.	What are the prevailing characteristics of partially nested designs, specifically regarding grouping structures, cluster assignment mechanisms, and sample size distributions?

Location of Partial Nesting:
```{r}
location_pn_dat <- full_experiment_dat |> 
  filter(partial_nest == "PN") |> 
  mutate(exp_TP = exp_treatment_provider_percent > 0 & exp_treatment_provider_percent < 1,
         exp_group = exp_treatment_group_percent > 0 & exp_treatment_group_percent < 1, 
         obs_TP = obs_treatment_group_percent > 0 & obs_treatment_group_percent < 1,
         obs_group = obs_treatment_group_percent > 0 & obs_treatment_group_percent < 1) |> 
  group_by(exp_level_random, journal_type) |> 
  summarise(across(matches("TP$|group$"), ~sum(.x, na.rm = TRUE)),
            total = n()) |> 
  ungroup()
location_pn_dat <- location_pn_dat |> 
  summarise(across(c(-exp_level_random, -journal_type), sum)) |> 
  mutate(exp_level_random = "Overall", journal_type = "Overall") |> 
  bind_rows(location_pn_dat)



location_pn_dat |>
  relocate(journal_type, exp_level_random) |> 
  rename(`Unit of Randomization` = exp_level_random,
         `Journal Type` = journal_type,
         `Unit of Analysis_Experimental_Treatment Provider` = exp_TP,
         `Unit of Analysis_Experimental_Group Setting` = exp_group,
         `Unit of Analysis_Observational_Treatment Provider` = obs_TP,
         `Unit of Analysis_Observational_Group Setting`= obs_group,
         `Number of Partial Nested Experiments` = total) |> 
  flextable() |> 
  separate_header()
  
```

Types of Partial nesting:

```{r}
type_partial_nesting_dat <- full_experiment_dat |> 
  filter(partial_nest == "PN") |> 
  group_by(partial_class, journal_type) |> 
  summarise(Total= n(),
            `Not Ignored` = sum(analytical_partial_cluster != "Ignored")) |> 
  pivot_wider(id_cols = partial_class,
              names_from = journal_type,
              values_from = c(Total, `Not Ignored`),
              names_glue = "{.value}_{journal_type}") |> 
  mutate(`Total_All` = Total_Education + Total_Health,
         `Not Ignored_All` = `Not Ignored_Education` + `Not Ignored_Health`) |> 
  ungroup()
type_partial_nesting_dat <- type_partial_nesting_dat |> 
  summarise(across(-partial_class, sum)) |> 
  mutate(partial_class = "Overall") |> 
  bind_rows(type_partial_nesting_dat)

type_partial_nesting_dat |> 
  arrange(desc(`Total_All`)) |> 
  relocate(partial_class, starts_with("Total"), starts_with("Not Ignored")) |> 
  rename(`PN Classification` = partial_class) |> 
  flextable() |> 
  separate_header()

```

Cluster Assignment Mechanism:
```{r}
full_experiment_dat |> 
  filter(partial_nest == "PN") |> 
  group_by(partial_assign_type, journal_type) |> 
  summarise(`Total`= n(),
            `Not Ignored` = sum(analytical_partial_cluster != "Ignored")) |> 
  ungroup() |> 
  complete(partial_assign_type, journal_type, fill = list(`Total` = 0)) |> 
  pivot_wider(id_cols = partial_assign_type,
              names_from = journal_type,
              values_from = c(`Total`),
              names_glue = "{journal_type}") |> 
  mutate(Overall = Education + Health)
```

## Research Question 3
3.	To what extent and by what statistical methods do researchers account for partial nesting?

## Research Question 4
4.	Among studies that account for partial nesting, how frequently and in what ways are cluster assignment mechanisms addressed in the analysis?

## Research Question 5
5.	What are possible reasons researchers might not account for partial nesting in their analyses?