---
title: "Tables and Figures"
format: docx
execute: 
  echo: false
  warning: false
---

```{r}
library(dplyr) #For general data manipulation
library(stringr) #For string manipulation
library(tidyr) #For pivoting
library(purrr)
library(flextable) # For Creating Tables
library(ggplot2)
full_experiment_dat <- read.csv(here::here("Analysis/Clean_Data/experimental_data.csv"))
screening_dat <- read.csv(here::here("Analysis/Clean_Data/screening_data.csv")) #Abstract and Full text screening data
full_experiment_dat <- full_experiment_dat |>
  mutate(
    analytical_partial_cluster_edit = case_when(
      study_id %in%
        c(
          "111568461", # All had clusters of size 1
          "111565034", # All had clusters of size 1
          "111576601", # All had clusters of size 1
          "111565413", # All had clusters of size 1
          "111565408" # All had clusters of size 1
        ) ~ "Ignored",
      study_id %in%
        c(
          "111575276", # Tested to see if clustering was present
          "111570022" #ICC calculated but ignored in treatment effect model
        ) ~ "Other",
      study_id %in% c("111571355") ~ "Ignored", #Discuss in limitations that clustering can be addressed in future study
      .default = analytical_partial_cluster
    )
  ) #These studies only have one partial cluster so coded them as ignored

long_cond <- read.csv(here::here("Analysis/Clean_Data/treatment_condition_data.csv"))
add_to_cond <- full_experiment_dat |>
  select(
    citation_id,
    study_id,
    response_id,
    experiment,
    exp_level_random,
    exp_random_procedure,
    partial_nest,
    partial_class,
    pub_journal,
    partial_standardization,
    partial_diversity,
    partial_standardization_diversity_source,
    partial_assign_type,
    partial_size
  )

long_cond <- long_cond |>
  left_join(
    add_to_cond,
    by = join_by(citation_id, study_id, response_id, experiment)
  )
```

```{r}
## Sample size cleaning for across conditions
# long_cond |>
#   filter(is.na(suppressWarnings(as.numeric(cond_exp_units_count)))) |>
#   View()

long_cond <- long_cond |>
  mutate(
    cond_exp_units_count_edit = case_when(
      str_detect(cond_exp_units_count, "\\*") ~ "Not Baseline",
      study_id %in% c("111573517", "111565447") ~ "Not Reported", #this study did not report their sample size
      study_id %in% c("111576847") & cond_name == "Standard Counseling" ~ "50", #Only the randomized part of the data
      is.na(suppressWarnings(as.numeric(
        cond_exp_units_count
      ))) ~ "Not Reported",
      .default = cond_exp_units_count
    )
  )

# long_cond |>
#   filter(exp_level_random == "Cluster") |>
#   filter(is.na(suppressWarnings(as.numeric(cond_obs_units_count)))) |>
#   View()

long_cond <- long_cond |>
  mutate(
    cond_obs_units_count_edit = case_when(
      exp_level_random == "Cluster" & study_id == "111565465" ~ str_remove(
        cond_obs_units_count,
        "\\*"
      ),
      exp_level_random == "Cluster" & study_id == "111571561" ~ "Not Baseline",
      exp_level_random == "Cluster" & study_id == "111571507" ~ "Not Reported",
      exp_level_random == "Cluster" &
        is.na(suppressWarnings(as.numeric(
          cond_obs_units_count
        ))) ~ "Multiple Types of Observation Units",
      .default = cond_obs_units_count
    )
  )
long_cond_sample_size <- long_cond |>
  mutate(
    cond_obs_units_count_edit_num = suppressWarnings(as.numeric(
      cond_obs_units_count_edit
    )),
    cond_exp_units_count_edit_num = suppressWarnings(as.numeric(
      cond_exp_units_count_edit
    ))
  ) |>
  ungroup()
```

```{r}
full_experiment_dat |>
  group_by(citation_id) |>
  summarise(number_study_published = n()) |>
  group_by(number_study_published) |>
  summarise(number_articles = n())
```

## Screening Process Stats

```{r}
screening_dat <- screening_dat |>
  mutate(
    full_text_screen = as.factor(replace_na(full_text_screen, "Ineligible"))
  ) |> #NA are those that were deemed ineligible at abstract phase
  mutate(
    journal_type = ifelse(
      toupper(journal_book_title) %in%
        c(
          "JOURNAL OF EDUCATIONAL RESEARCH",
          "JOURNAL OF EDUCATIONAL PSYCHOLOGY",
          "JOURNAL OF RESEARCH ON EDUCATIONAL EFFECTIVENESS"
        ),
      "Education",
      "Health"
    )
  ) |>
  mutate(
    pred = factor("Eligible", levels = c("Eligible", "Ineligible")),
    pred_13 = as.factor(ifelse(Score >= 13, "Eligible", "Ineligible"))
  )
```

```{r}
library(yardstick)
roc_curve(screening_dat, full_text_screen, Score) |>
  ggplot(aes(x = 1 - specificity, y = sensitivity)) +
  geom_path() +
  geom_abline(lty = 3) +
  coord_equal() +
  theme_bw()
conf_mat(screening_dat, truth = full_text_screen, estimate = pred) |>
  summary()
conf_mat(screening_dat, truth = full_text_screen, estimate = pred_13) |>
  summary()

roc_curve(screening_dat, full_text_screen, Score) |>
  mutate(j_index = sensitivity + specificity - 1) %>%
  slice_max(j_index, with_ties = FALSE)

roc_auc_vec(
  truth = as.factor(screening_dat$full_text_screen),
  estimate = screening_dat$Score
)

screening_dat |>
  nest_by(journal_type) |>
  mutate(roc_dat = list(roc_curve(data, full_text_screen, Score))) |>
  select(-data) |>
  unnest(roc_dat) |>
  ggplot(aes(x = 1 - specificity, y = sensitivity, colour = journal_type)) +
  geom_path() +
  geom_abline(lty = 3) +
  coord_equal() +
  theme_bw()
```



## Article Characteristics 
* Year of publication
* Types of Randomization procedure
* Number of Experimental Conditions
* Number of primary or secondary analysis
* Sample size
```{r}
calc_freq <- function(experimental_dat, variable) {
  var_label <- deparse(substitute(variable))
  full_experiment_dat |>
    group_by({{ variable }}) |>
    summarise(count = n()) |>
    rename(variable = {{ variable }}) |>
    mutate(across(everything(), as.character)) |>
    bind_rows(data.frame(variable = var_label, count = NA)) |>
    arrange(!is.na(count))
}


exp_characteristics <- bind_rows(
  calc_freq(full_experiment_dat, partial_nest),
  calc_freq(full_experiment_dat, pub_year),
  calc_freq(full_experiment_dat, exp_level_random),
  calc_freq(full_experiment_dat, exp_random_procedure),
  calc_freq(full_experiment_dat, pub_primary_secondary)
)
exp_characteristics <- exp_characteristics |>
  mutate(
    variable = case_when(
      variable == "partial_nest" ~ "Partial Nesting Present",
      variable == "No-PN" ~ "No",
      variable == "PN" ~ "Yes",
      variable == "pub_year" ~ "Publication Year",
      variable == "exp_level_random" ~ "Level of Randomization",
      variable == "exp_random_procedure" ~ "Randomization Procedure",
      variable == "pub_primary_secondary" ~ "Source",
      .default = variable
    )
  ) |>
  rename(
    Characteristic = variable,
    !!str_glue(
      "Number of Experiments (n = {nrow(full_experiment_dat)})"
    ) := count
  )

exp_characteristics |>
  flextable() |>
  padding(
    i = ~ !(Characteristic %in%
      c(
        "Partial Nesting Present",
        "Publication Year",
        "Level of Randomization",
        "Randomization Procedure",
        "Source"
      )),
    j = "Characteristic",
    padding.left = 20
  ) |>
  autofit() |>
  font(font = "Times New Roman", part = "all") |>
  border_remove() |>
  hline_bottom(part = "body") |>
  hline_top(part = "body") |>
  hline_top(part = "header")
```

Sample size per randomized condition:
```{r}
# cluster randomized
sample_size_info <- long_cond_sample_size |>
  filter(
    (exp_level_random == "Cluster" &
      !is.na(cond_exp_units_count_edit_num) &
      !is.na(cond_obs_units_count_edit_num)) |
      (exp_level_random == "Individual" &
        !is.na(cond_exp_units_count_edit_num))
  ) |>
  select(
    study_id,
    experiment,
    exp_level_random,
    cond_type,
    partial_nest,
    cond_exp_units_count_edit_num,
    cond_obs_units_count_edit_num
  )

sample_size_stat <- sample_size_info |>
  group_by(partial_nest, exp_level_random) |>
  summarise(
    across(
      .cols = c(cond_exp_units_count_edit_num, cond_obs_units_count_edit_num),
      .fns = list(
        min = ~ min(.x, na.rm = TRUE),
        q25 = ~ quantile(.x, probs = .25, na.rm = TRUE),
        med = ~ median(.x, na.rm = TRUE),
        q75 = ~ quantile(.x, probs = .75, na.rm = TRUE),
        max = ~ max(.x, na.rm = TRUE),
        mean = ~ mean(.x, na.rm = TRUE),
        sd = ~ sd(.x, na.rm = TRUE)
      )
    ),
    num_exp = n_distinct(study_id, experiment)
  ) |>
  pivot_longer(
    cols = c(-partial_nest, -num_exp, -exp_level_random),
    names_to = c("unit_type", ".value"),
    names_pattern = "cond_(exp|obs)_units_count_edit_num_(.*)"
  ) |>
  filter(!(exp_level_random == "Individual" & unit_type == "obs"))


## Formating  -----
sample_size_format <- sample_size_stat |>
  arrange(exp_level_random, desc(partial_nest)) |>
  mutate(
    unit_type = case_when(
      unit_type == "exp" ~ "Experimental",
      unit_type == "obs" ~ "Observational"
    )
  ) |>
  relocate(exp_level_random, partial_nest, unit_type) |>
  rename(
    `Type of Unit` = unit_type,
    `Level of Randomization` = exp_level_random,
    `Partial Nesting` = partial_nest,
    `Number of Experiments` = num_exp,
    Min = min,
    `25th Quartile` = q25,
    Median = med,
    `75th Quartile` = q75,
    Max = max,
    Mean = mean,
    SD = sd
  )

sample_size_format |>
  flextable() |>
  colformat_double(digits = 1) |>
  autofit() |>
  font(font = "Times New Roman", part = "all") |>
  border_remove() |>
  hline_bottom(part = "body") |>
  hline_top(part = "body") |>
  hline_top(part = "header")
```


## Research Question 1 
1.	How prevalent are partial nested designs among randomized experiments in education and public health research?

```{r}
count_articles <- function(experimental_dat, ...) {
  #... is the grouping variable for journal type or specific publication journal
  experimental_dat |>
    group_by(exp_level_random, partial_nest, ...) |>
    summarise(count = n()) |>
    mutate(
      experiment_type = paste(exp_level_random, partial_nest, sep = "_")
    ) |>
    pivot_wider(
      id_cols = c(...),
      names_from = experiment_type,
      values_from = count
    ) |>
    mutate(across(everything(), ~ ifelse(is.na(.x), 0, .x)))
}
counts_publication <- count_articles(
  full_experiment_dat,
  journal_type,
  pub_journal
)
counts_journal_type <- count_articles(full_experiment_dat, journal_type) |>
  mutate(pub_journal = journal_type)
counts_marginal <- count_articles(full_experiment_dat) |>
  mutate(pub_journal = "Overall", journal_type = "Overall")
stopifnot(!("Mix_No-PN" %in% names(counts_publication))) #If this fails then remove line of code that adds this column in

number_exp_dat <- bind_rows(
  counts_publication,
  counts_journal_type,
  counts_marginal
) |>
  ungroup() |>
  mutate(`Mix_No-PN` = 0) |> ## Remove this line if Mix_Non-PN are found
  rowwise() |>
  mutate(
    Cluster_Total = sum(c_across(starts_with("Cluster"))),
    Individual_Total = sum(c_across(starts_with("Individual"))),
    Mix_Total = sum(c_across(starts_with("Mix"))),
    `All Designs_Total` = sum(c_across(ends_with("Total"))),
    `All Designs_PN` = sum(c_across(ends_with("_PN")))
  ) |>
  ungroup()

number_exp_dat |>
  arrange(desc(journal_type), desc(`All Designs_Total`)) |>
  select(-journal_type, pub_journal, -contains("No-PN")) |>
  relocate(
    pub_journal,
    starts_with("Individual"),
    starts_with("Cluster"),
    starts_with("Mix"),
    `All Designs_PN`,
    `All Designs_Total`
  ) |>
  rename(Publication = pub_journal) |>
  flextable() |>
  separate_header() |>
  align(align = "center", part = "header") |>
  padding(
    i = ~ !(Publication %in% c("Overall", "Health", "Education")),
    j = "Publication",
    padding.left = 20
  ) |>
  add_header_row(
    values = c("", "Level of Randomization", ""),
    colwidths = c(1, 6, 2)
  ) |>
  autofit() |>
  font(font = "Times New Roman", part = "all") |>
  border_remove() |>
  hline_bottom(part = "body") |>
  hline_top(part = "body") |>
  hline_top(part = "header")
```


```{r}
# long_cond |>
#   relocate(study_id, pub_journal, partial_class) |>
#   dataviewR::dataviewer()
# dataviewR::stop_all_dataviewers()
# ```
```

```{r}
# full_experiment_dat |>
#   relocate(study_id, pub_journal, partial_class) |>
#   dataviewR::dataviewer()
```

## Research Question 2
2.	What are the prevailing characteristics of partially nested designs, specifically regarding grouping structures, cluster assignment mechanisms, and sample size distributions?

Location of Partial Nesting:
```{r}
location_pn_dat <- full_experiment_dat |>
  filter(partial_nest == "PN") |>
  mutate(
    exp_TP = exp_treatment_provider_percent > 0 &
      exp_treatment_provider_percent < 1,
    exp_group = exp_treatment_group_percent > 0 &
      exp_treatment_group_percent < 1,
    obs_TP = obs_treatment_provider_percent > 0 &
      obs_treatment_provider_percent < 1,
    obs_group = obs_treatment_group_percent > 0 &
      obs_treatment_group_percent < 1
  ) |>
  mutate(
    partial_class = case_when(
      study_id == "111571561" ~ "Complex", #Teachers had coaches and  professional course in different treatment conditons that gets comlapsed
      study_id == "111568439" ~ "Complex", #coaches and group intervention across different treatment conditions
      study_id == "111568554" ~ "Complex", #One treatment conditon had treatment providers one had group training class.
      study_id == "111571616" ~ "Other", # Had students paired in treatment arm multiple times, Partial clusters that change overtime
      exp_level_random == "Mix" ~ "Other", #Unclear
      exp_group ~ "Grouped",
      !exp_group & exp_TP ~ "Treatment Provider",
      !exp_group & !exp_TP & obs_group ~ "Observational Grouped",
      !exp_group &
        !exp_TP &
        !obs_group &
        obs_TP ~ "Observational Treatment Provider",
      .default = "Complex"
    )
  )


new_partial_classes <- location_pn_dat |>
  select(study_id, experiment, partial_class)

long_cond_sample_size <- long_cond_sample_size |> #replacing old partial classes
  select(-partial_class) |>
  left_join(new_partial_classes)
```

```{r}
location_pn_dat_stat <- location_pn_dat |>
  group_by(
    exp_level_random,
    partial_class,
    exp_TP,
    exp_group,
    obs_TP,
    obs_group
  ) |>
  summarise(Count = n()) |>
  ungroup()


location_pn_dat_stat |>
  mutate(across(
    c(-exp_level_random, -partial_class, -Count),
    .fns = ~ ifelse(.x == FALSE, NA, "x")
  )) |>
  relocate(
    exp_level_random,
    partial_class,
    exp_group,
    exp_TP,
    obs_group,
    obs_TP,
    Count
  ) |>
  arrange(exp_level_random, exp_group, exp_TP, obs_group, obs_TP) |>
  rename(
    `Level of Randomization` = exp_level_random,
    `Type of Partial Nesting` = partial_class,
    `Experimental Unit_Treatment Provider Present` = exp_TP,
    `Experimental Unit_Group Setting Present` = exp_group,
    `Observational Unit_Treatment Provider Present` = obs_TP,
    `Observational Unit_Group Setting Present` = obs_group,
    `Number of Experiments` = Count
  ) |>
  flextable() |>
  separate_header() |>
  autofit() |>
  font(font = "Times New Roman", part = "all") |>
  border_remove() |>
  hline_bottom(part = "body") |>
  hline_top(part = "body") |>
  hline_top(part = "header")
```


Sample Size of partial clusters:
```{r}
explore_samplesize <- long_cond_sample_size |>
  filter(
    partial_nest == "PN",
    partial_class != "Complex",
    partial_class != "Other"
  ) |>
  mutate(
    partial_cluster_sample_size = case_when(
      partial_class == "Treatment Provider" ~ cond_treatment_provider_num,
      partial_class == "Grouped" ~ cond_treatment_groups_num,
      partial_class ==
        "Observational Treatment Provider" ~ cond_treatment_provider_num,
      partial_class == "Observational Grouped" ~ cond_treatment_groups_num
    )
  ) |>
  mutate(
    relevant_unit_size = case_when(
      study_id == "111565404" ~ 100, #100 students are placed into teams
      study_id == "111565472" ~ 1835, #1836 math students nested within 70 math teachers whom did 58 group settings
      partial_class == "Treatment Provider" ~ cond_exp_units_count_edit_num,
      partial_class == "Grouped" ~ cond_exp_units_count_edit_num,
      partial_class ==
        "Observational Treatment Provider" ~ cond_obs_units_count_edit_num,
      partial_class == "Observational Grouped" ~ cond_obs_units_count_edit_num
    )
  ) |>
  filter(!is.na(partial_cluster_sample_size)) |> #Removes treatment conditions that did not have partial nesting
  mutate(
    partial_cluster_sample_size = case_when(
      study_id == 111566857 ~ "Unclear", #This study did involve tutors in a group setting but unclear if students were always in the same group
      study_id == 111571616 ~ "Unclear", #Random pairs throughout the semester))
      .default = partial_cluster_sample_size
    )
  ) |>
  mutate(
    partial_cluster_sample_size = case_when(
      study_id == 111568543 ~ "9*", #Total number of coaches across all conditions since 6 are shared and 3 are unique to their condition
      .default = partial_cluster_sample_size
    )
  ) |>
  rowwise() |>
  mutate(
    partial_cluster_sample_size_edit = case_when(
      str_detect(partial_cluster_sample_size, "\\*") ~ str_remove(
        partial_cluster_sample_size,
        "\\*"
      ), #remove *
      str_detect(
        partial_cluster_sample_size,
        "-"
      ) ~ as.character(round(mean(suppressWarnings(as.numeric(unlist(str_split(
        partial_cluster_sample_size,
        "-"
      ))))))), #Find the mid point
      study_id == 111573573 ~ "6", #The max number of groups
      study_id == 111577860 ~ "9", #The Min number of treatment providers
      study_id == 111567874 ~ "18", #Max number of groups
      .default = partial_cluster_sample_size
    )
  )

explore_samplesize <- explore_samplesize |>
  group_by(study_id, experiment) |>
  mutate(
    relevant_unit_size_edit = case_when(
      str_detect(partial_cluster_sample_size, "\\*") ~ sum(relevant_unit_size),
      .default = relevant_unit_size
    )
  ) |>
  ungroup() |>
  mutate(
    partial_class = ifelse(
      partial_cluster_sample_size_edit == 1,
      "Single",
      partial_class
    )
  )
```

```{r}
add_PC_sample_size_to_experiment <- explore_samplesize |>
  select(
    citation_id,
    study_id,
    response_id,
    experiment,
    partial_cluster_sample_size,
    relevant_unit_size
  ) |>
  group_by(citation_id, study_id, response_id, experiment) |>
  summarise(
    partial_cluster_sample_size = paste(
      partial_cluster_sample_size,
      collapse = ","
    ),
    relevant_unit_size = paste(relevant_unit_size, collapse = ",")
  )


location_pn_dat <- location_pn_dat |>
  left_join(select(
    add_PC_sample_size_to_experiment,
    citation_id,
    study_id,
    response_id,
    experiment,
    partial_cluster_sample_size,
    relevant_unit_size
  )) |>
  mutate(
    partial_class = case_when(
      str_detect(partial_cluster_sample_size, "^1$") |
        str_detect(partial_cluster_sample_size, "^1\\*") ~ "Single",
      .default = partial_class
    )
  )

nrow(distinct(location_pn_dat))
```

Grouping Structures of Partial Nesting

```{r}
partial_class_by_level_journal_class <- location_pn_dat |>
  group_by(exp_level_random, partial_class, journal_type) |>
  summarise(Total = n())

partial_class_by_level_journal <- location_pn_dat |>
  group_by(exp_level_random, journal_type) |>
  summarise(Total = n()) |>
  mutate(partial_class = "Overall")

partial_class_by_journal <- location_pn_dat |>
  group_by(journal_type) |>
  summarise(
    Total = n()
  ) |>
  mutate(partial_class = "", exp_level_random = "Overall")

partial_class_stats <- bind_rows(
  partial_class_by_level_journal_class,
  partial_class_by_level_journal,
  partial_class_by_journal
) |>
  pivot_wider(
    id_cols = c(exp_level_random, partial_class),
    names_from = journal_type,
    values_from = Total
  ) |>
  mutate(across(everything(), ~ replace_na(.x, 0))) |>
  mutate(Overall = Education + Health) |>
  mutate(
    exp_level_random = factor(
      exp_level_random,
      levels = c("Overall", "Cluster", "Individual", "Mix")
    ),
    partial_class = factor(
      partial_class,
      levels = c(
        "Overall",
        "Grouped",
        "Treatment Provider",
        "Observational Grouped",
        "Observational Treatment Provider",
        "Complex",
        "Other",
        "Single"
      )
    )
  )
```

```{r}
partial_class_stats |>
  arrange(exp_level_random, partial_class) |>
  relocate(
    exp_level_random,
    partial_class,
    starts_with("Education"),
    starts_with("Health"),
    starts_with("Overall")
  ) |>
  rename(
    `Partial Nesting Classification` = partial_class,
    `Level of Randomization` = exp_level_random
  ) |>
  flextable() |>
  padding(
    i = ~ !(`Partial Nesting Classification` %in% c("Overall")),
    j = "Partial Nesting Classification",
    padding.left = 20
  ) |>
  separate_header() |>
  autofit() |>
  font(font = "Times New Roman", part = "all") |>
  border_remove() |>
  hline_bottom(part = "body") |>
  hline_top(part = "body") |>
  hline_top(part = "header")
```

Cluster Assignment Mechanism:

```{r}
location_pn_dat <- location_pn_dat |>
  filter(partial_class != "Single")

location_pn_dat <- location_pn_dat |>
  mutate(
    partial_assign_type_edit = case_when(
      str_detect(partial_cluster_sample_size, "^1$") |
        str_detect(partial_cluster_sample_size, "^1\\*") ~ "Single",
      partial_assign_type == "Natural (Non-Random)" ~ "Non-Random",
      partial_assign_type ==
        "Natural within Blocks/Strata" ~ "Non-Random within Blocks/Strata",
      is.na(partial_cluster_sample_size) ~ partial_assign_type,
      .default = partial_assign_type
    ),
    analytical_partial_cluster_edit = case_when(
      str_detect(partial_cluster_sample_size, "^1$") |
        str_detect(partial_cluster_sample_size, "^1\\*") ~ "Single",
      .default = analytical_partial_cluster_edit
    )
  )

cluster_assignment_stat <- location_pn_dat |>
  group_by(partial_class, partial_assign_type_edit) |>
  summarise(number_of_experiments = n()) |>
  pivot_wider(
    id_cols = c(partial_assign_type_edit),
    names_from = c(partial_class),
    values_from = number_of_experiments
  ) |>
  mutate(across(everything(), ~ replace_na(.x, 0))) |>
  mutate(Total = rowSums(across(-partial_assign_type_edit))) |>
  ungroup()

order_cluster_assignment <- c(
  "Overall",
  "Non-Random",
  "Non-Random within Blocks/Strata",
  "Randomized",
  "Randomized within Blocks/Strata",
  "Matching",
  "Other",
  "Single"
)

overall_cluster_assignment_stat <- cluster_assignment_stat |>
  summarise(across(c(-partial_assign_type_edit), sum)) |>
  mutate(partial_assign_type_edit = "Overall")

cluster_assignment_stat |>
  bind_rows(overall_cluster_assignment_stat) |>
  mutate(
    partial_assign_type_edit = factor(
      partial_assign_type_edit,
      levels = order_cluster_assignment
    )
  ) |>
  arrange(partial_assign_type_edit) |>
  relocate(
    partial_assign_type_edit,
    Total,
    `Treatment Provider`,
    Grouped,
    `Observational Grouped`,
    `Observational Treatment Provider`,
    Complex,
    Other
  ) |>
  rename(`Cluster Assignment Type` = partial_assign_type_edit) |>
  flextable() |>
  separate_header() |>
  padding(
    i = ~ !(`Cluster Assignment Type` %in% c("Overall")),
    j = "Cluster Assignment Type",
    padding.left = 20
  ) |>
  add_header_row(
    values = c("", "Partial Nesting Classification"),
    colwidths = c(2, 6)
  ) |>
  align(align = "center", part = "header") |>
  autofit() |>
  font(font = "Times New Roman", part = "all") |>
  border_remove() |>
  hline_bottom(part = "body") |>
  hline_top(part = "body") |>
  hline_top(part = "header") |>
  hline(i = 1, j = 3:8, part = "header")
```

```{r}
location_pn_dat |>
  filter(
    exp_level_random == "Cluster",
    partial_class == "Treatment Provider"
  ) |>
  with(table(exp_exp_unit))
```

Reporting of Partial clusters size:
```{r}
table(location_pn_dat$partial_size)
table(location_pn_dat$partial_size, location_pn_dat$partial_class)
```

Reporting number of partial clusters

```{r}
long_cond_report_num_PC <- long_cond_sample_size |>
  filter(partial_nest == "PN") |>
  filter(
    !is.na(cond_treatment_provider_num) | !is.na(cond_treatment_groups_num)
  ) |> #Removes treatment conditions that do not have any treatment nesting
  mutate(
    partial_cluster_report_num = case_when(
      #Indicator if any information is given around the number of partial clusters
      str_detect(toupper(cond_treatment_groups_num), "^NOT|^NOR|UNCLEAR") &
        str_detect(
          toupper(cond_treatment_provider_num),
          "^NOT|^NOR|UNCLEAR"
        ) ~ FALSE,
      partial_class == "Treatment Provider" ~ !str_detect(
        toupper(cond_treatment_provider_num),
        "^NOT|^NOR|UNCLEAR"
      ),
      partial_class == "Grouped" ~ !str_detect(
        toupper(cond_treatment_groups_num),
        "^NOT|^NOR|UNCLEAR"
      ),
      partial_class == "Observational Treatment Provider" ~ !str_detect(
        toupper(cond_treatment_provider_num),
        "^NOT|^NOR|UNCLEAR"
      ),
      partial_class == "Observational Grouped" ~ !str_detect(
        toupper(cond_treatment_groups_num),
        "^NOT|^NOR|UNCLEAR"
      ),
      partial_class == "Complex" ~ ifelse(partial_size == "Yes", TRUE, NA), #If size is not reported need to judge if number of partial clusters is reported
      partial_class == "Other" ~ ifelse(partial_size == "Yes", TRUE, NA)
    )
  ) |> #If size is not reported need to judge if number of partial clusters is reported
  mutate(
    partial_cluster_report_num = case_when(
      #manually fixing those that have NA
      study_id == "111571616" ~ FALSE, #Individual Programming vs Pair programming with three combinations of pairs
      study_id == "111565397" ~ TRUE, #this experiment reported the number of group settings
      study_id == "111570010" ~ FALSE, #Does not report number of treatment provider or size
      .default = partial_cluster_report_num
    )
  )
partial_nest_report_num_dat <- long_cond_report_num_PC |>
  group_by(study_id, experiment) |>
  summarise(exp_report_info = sum(partial_cluster_report_num) >= 1)

table(partial_nest_report_num_dat$exp_report_info)
```



Trying to summarise across experiments
number of experiments that did not report the number of partial clusters or size of partial clusters to calculate the number. 
number it is unclear due to the particular design characteristics 
number of experiments with just 1 partial cluster. 

```{r}
pc_samplesize_types <- explore_samplesize |>
  group_by(exp_level_random, partial_class, study_id, experiment) |> #Sums across treatment conditions so that each row is experiment
  summarise(
    studies_no_report = sum(str_detect(
      tolower(partial_cluster_sample_size_edit),
      "report"
    )),
    studies_unclear = sum(str_detect(
      tolower(partial_cluster_sample_size_edit),
      "unclear"
    )),
    studies_report_calculate = sum(str_detect(
      partial_cluster_sample_size_edit,
      "^\\d+(\\.\\d+)?$"
    ))
  ) |>
  group_by(exp_level_random, partial_class) |>
  summarise(
    experiments_no_report = sum(studies_no_report != 0),
    experiments_unclear = sum(studies_unclear != 0),
    experiments_report = sum(studies_report_calculate != 0),
    experiments_total = n()
  ) |>
  ungroup()
pc_samplesize_types_stat <- pc_samplesize_types |>
  summarise(across(starts_with("experiments"), sum)) |>
  mutate(partial_class = "Total") |>
  bind_rows(pc_samplesize_types)
```



For experiments that did report the number of partial clusters. For students that report both ratio of 
For each type of partial class mean, median, min, max, lower_quartile, upper_quartile



```{r}
pc_samplesize_exp <- explore_samplesize |>
  filter(partial_class != "Single") |>
  mutate(
    partial_cluster_sample_size_edit_num = suppressWarnings(as.numeric(
      partial_cluster_sample_size_edit
    ))
  ) |>
  mutate(
    unit_per_pc = relevant_unit_size_edit / partial_cluster_sample_size_edit_num
  ) |>
  group_by(exp_level_random, partial_class, study_id, experiment) |>
  summarise(
    average_unit_pc = mean(unit_per_pc, na.rm = TRUE), #average across treatment conditions
    mean_pc = mean(partial_cluster_sample_size_edit_num, na.rm = TRUE)
  ) |>
  mutate(
    average_unit_pc = case_when(
      study_id == 111571690 ~ 17.5, #This study the observational unit is students but groups were made with teachers so this reflects the number of teachers in the study reather then the number of students under their care
      .default = average_unit_pc
    ),
    mean_pc = case_when(study_id == 111571690 ~ 32, .default = mean_pc)
  ) |>
  ungroup() |>
  filter(!is.na(average_unit_pc), !is.na(mean_pc)) #Removes studies that did not report number of partial clusters or size of partial clusters

pc_samplesize_stat <- pc_samplesize_exp |>
  group_by(exp_level_random, partial_class) |>
  summarise(
    across(
      .cols = c(average_unit_pc, mean_pc),
      .fns = list(
        min = ~ min(.x, na.rm = TRUE),
        q25 = ~ quantile(.x, probs = .25, na.rm = TRUE),
        med = ~ median(.x, na.rm = TRUE),
        q75 = ~ quantile(.x, probs = .75, na.rm = TRUE),
        max = ~ max(.x, na.rm = TRUE),
        mean = ~ mean(.x, na.rm = TRUE),
        sd = ~ sd(.x, na.rm = TRUE)
      )
    ),
    number_experiments = sum(!is.na(average_unit_pc))
  )

pc_samplesize_stat_design <- pc_samplesize_exp |>
  group_by(exp_level_random) |>
  summarise(
    across(
      .cols = c(average_unit_pc, mean_pc),
      .fns = list(
        min = ~ min(.x, na.rm = TRUE),
        q25 = ~ quantile(.x, probs = .25, na.rm = TRUE),
        med = ~ median(.x, na.rm = TRUE),
        q75 = ~ quantile(.x, probs = .75, na.rm = TRUE),
        max = ~ max(.x, na.rm = TRUE),
        mean = ~ mean(.x, na.rm = TRUE),
        sd = ~ sd(.x, na.rm = TRUE)
      )
    ),
    number_experiments = sum(!is.na(average_unit_pc))
  ) |>
  mutate(partial_class = "Overall")


pc_samplesize_stat_overall <- pc_samplesize_exp |>
  summarise(
    across(
      .cols = c(average_unit_pc, mean_pc),
      .fns = list(
        min = ~ min(.x, na.rm = TRUE),
        q25 = ~ quantile(.x, probs = .25, na.rm = TRUE),
        med = ~ median(.x, na.rm = TRUE),
        q75 = ~ quantile(.x, probs = .75, na.rm = TRUE),
        max = ~ max(.x, na.rm = TRUE),
        mean = ~ mean(.x, na.rm = TRUE),
        sd = ~ sd(.x, na.rm = TRUE)
      )
    ),
    number_experiments = sum(!is.na(average_unit_pc))
  ) |>
  mutate(exp_level_random = "Overall", partial_class = "")

pc_samplesize_stat_summary <- bind_rows(
  pc_samplesize_stat,
  pc_samplesize_stat_design,
  pc_samplesize_stat_overall
)
```


Average units per partial cluster:

```{r}
pc_samplesize_stat_summary |>
  select(
    exp_level_random,
    partial_class,
    number_experiments,
    starts_with("average_unit_pc")
  ) |>
  mutate(
    exp_level_random = factor(
      exp_level_random,
      levels = c("Overall", "Cluster", "Individual")
    ),
    partial_class = factor(
      partial_class,
      levels = c(
        "Overall",
        "Grouped",
        "Observational Grouped",
        "Treatment Provider",
        "Observational Treatment Provider"
      )
    )
  ) |>
  arrange(exp_level_random, partial_class) |>
  rename(
    `Number of Experiments` = number_experiments,
    `Level of Randomization` = exp_level_random,
    `Partial Nesting Classification` = partial_class,
    Min = average_unit_pc_min,
    `25th Quartile` = average_unit_pc_q25,
    Mean = average_unit_pc_mean,
    SD = average_unit_pc_sd,
    Median = average_unit_pc_med,
    `75th Quartile` = average_unit_pc_q75,
    Max = average_unit_pc_max
  ) |>
  relocate(
    `Level of Randomization`,
    `Partial Nesting Classification`,
    `Number of Experiments`,
    everything()
  ) |>
  flextable() |>
  padding(
    i = ~ !(`Partial Nesting Classification` %in% c("Overall")),
    j = "Partial Nesting Classification",
    padding.left = 20
  ) |>
  colformat_double() |>
  separate_header() |>
  autofit() |>
  font(font = "Times New Roman", part = "all") |>
  border_remove() |>
  hline_bottom(part = "body") |>
  hline_top(part = "body") |>
  hline_top(part = "header")
```

Number of partial clusters 
```{r}
pc_samplesize_stat_summary |>
  select(
    exp_level_random,
    partial_class,
    number_experiments,
    starts_with("mean_pc")
  ) |>
  mutate(
    exp_level_random = factor(
      exp_level_random,
      levels = c("Overall", "Cluster", "Individual")
    ),
    partial_class = factor(
      partial_class,
      levels = c(
        "Overall",
        "Grouped",
        "Observational Grouped",
        "Treatment Provider",
        "Observational Treatment Provider"
      )
    )
  ) |>
  arrange(exp_level_random, partial_class) |>
  rename(
    `Number of Experiments` = number_experiments,
    `Level of Randomization` = exp_level_random,
    `Partial Nesting Classification` = partial_class,
    Min = mean_pc_min,
    `25th Quartile` = mean_pc_q25,
    Mean = mean_pc_mean,
    SD = mean_pc_sd,
    Median = mean_pc_med,
    `75th Quartile` = mean_pc_q75,
    Max = mean_pc_max
  ) |>
  relocate(
    `Level of Randomization`,
    `Partial Nesting Classification`,
    `Number of Experiments`,
    everything()
  ) |>
  flextable() |>
  padding(
    i = ~ !(`Partial Nesting Classification` %in% c("Overall")),
    j = "Partial Nesting Classification",
    padding.left = 20
  ) |>
  colformat_double() |>
  separate_header() |>
  autofit() |>
  font(font = "Times New Roman", part = "all") |>
  border_remove() |>
  hline_bottom(part = "body") |>
  hline_top(part = "body") |>
  hline_top(part = "header")
```


## Research Question 3
3.	To what extent and by what statistical methods do researchers account for partial nesting? Among studies that account for partial nesting, how frequently and in what ways are cluster assignment mechanisms addressed in the analysis?

Accounting for Parital Nesting by journal type and PN Classification

```{r}
cluster_treated_dat <- full_experiment_dat |>
  filter(exp_level_random == "Cluster") |>
  mutate(
    cluster_treatment = str_remove(
      #Remove the characteirsitcs that realte to other types of hiearchicy
      analytical_hierarchcial,
      ",Fixed effects|Fixed effects,|,Other|,Ignored"
    )
  ) |>
  mutate(
    cluster_treatment = case_when(
      study_id == 111566800 ~ "Ignored", #Used robust variance at the classroom level but not randomized levevl site
      study_id == 111570002 ~ "Single", #Only had 1 cluster per condition,
      study_id == 111565404 ~ "Single", #only had 1 cluster per condition, they did random effects within the randomization site
      .default = cluster_treatment
    )
  ) |>
  mutate(
    cluster_treatment_address = ifelse(
      cluster_treatment %in% c("Fixed Effects", "Ignored", "Single"),
      "Did Not Address Clustering",
      "Addressed Clustering"
    )
  )

# cluster_treated_dat |>
#   select(
#     study_id,
#     exp_exp_unit,
#     analytical_hierarchcial,
#     analytical_dep_detail,
#     analytical_comments,
#     cluster_treatment
#   ) |>
#   View()
```

```{r}
cluster_treat_journal_type <- cluster_treated_dat |>
  group_by(journal_type, cluster_treatment) |>
  summarise(count = n()) |>
  group_by(journal_type) |>
  mutate(journal_type = str_glue("{journal_type} (N = {sum(count)})"))

cluster_treat_overall <- cluster_treated_dat |>
  group_by(cluster_treatment) |>
  summarise(count = n()) |>
  mutate(journal_type = "Overall") |>
  group_by(journal_type) |>
  mutate(journal_type = str_glue("{journal_type} (N = {sum(count)})"))


cluster_treat_address <- cluster_treated_dat |>
  group_by(journal_type, cluster_treatment_address) |>
  summarise(count = n()) |>
  group_by(journal_type) |>
  mutate(journal_type = str_glue("{journal_type} (N = {sum(count)})")) |>
  rename(cluster_treatment = cluster_treatment_address)

cluster_treat_address_overall <- cluster_treated_dat |>
  group_by(cluster_treatment_address) |>
  summarise(count = n()) |>
  mutate(journal_type = "Overall") |>
  group_by(journal_type) |>
  mutate(journal_type = str_glue("{journal_type} (N = {sum(count)})")) |>
  rename(cluster_treatment = cluster_treatment_address)


cluster_treat_summary <- bind_rows(
  cluster_treat_overall,
  cluster_treat_journal_type,
  cluster_treat_address,
  cluster_treat_address_overall
) |>
  pivot_wider(
    id_cols = c(cluster_treatment),
    names_from = journal_type,
    values_from = c(count),
    names_glue = "{journal_type}"
  )
```

Cluster treatment in CRD designs

```{r}
cluster_treat_levels <- sort(cluster_treat_summary$cluster_treatment)[
  !(sort(cluster_treat_summary$cluster_treatment) %in%
    c(
      "Did Not Address Clustering",
      "Fixed effects",
      "Ignored",
      "Other",
      "Single"
    ))
]


cluster_treat_levels <- c(
  cluster_treat_levels,
  "Other",
  "Did Not Address Clustering",
  "Fixed effects",
  "Ignored",
  "Single"
)
cluster_treat_summary |>
  mutate(
    cluster_treatment = factor(
      cluster_treatment,
      levels = cluster_treat_levels
    )
  ) |>
  arrange(cluster_treatment) |>
  mutate(across(everything(), ~ replace_na(.x, 0))) |>
  relocate(
    cluster_treatment,
    starts_with("Education"),
    starts_with("Health"),
    starts_with("Overall")
  ) |>
  mutate(cluster_treatment = str_replace(cluster_treatment, ",", " & ")) |>
  rename(`Analytical Approach` = cluster_treatment) |>
  flextable() |>
  padding(
    i = ~ !(`Analytical Approach` %in%
      c("Addressed Clustering", "Did Not Address Clustering")),
    j = "Analytical Approach",
    padding.left = 20
  ) |>
  separate_header() |>
  autofit() |>
  font(font = "Times New Roman", part = "all") |>
  border_remove() |>
  hline_bottom(part = "body") |>
  hline_top(part = "body") |>
  hline_top(part = "header")
```

Ignoring Partial Clusters

```{r}
not_ignored_analytical <- location_pn_dat |>
  filter(analytical_partial_cluster_edit != "Single") |>
  group_by(exp_level_random, partial_class, journal_type) |>
  summarise(
    Total = n(),
    `Not Ignored` = sum(analytical_partial_cluster_edit != "Ignored")
  )

not_ignored_analytical_overall_design <- location_pn_dat |>
  filter(analytical_partial_cluster_edit != "Single") |>
  group_by(exp_level_random, journal_type) |>
  summarise(
    Total = n(),
    `Not Ignored` = sum(analytical_partial_cluster_edit != "Ignored")
  ) |>
  mutate(partial_class = "Overall")

not_ignored_analytical_overall <- location_pn_dat |>
  filter(analytical_partial_cluster_edit != "Single") |>
  group_by(journal_type) |>
  summarise(
    Total = n(),
    `Not Ignored` = sum(analytical_partial_cluster_edit != "Ignored")
  ) |>
  mutate(partial_class = "", exp_level_random = "Overall")

not_ignored_summary <- bind_rows(
  not_ignored_analytical,
  not_ignored_analytical_overall_design,
  not_ignored_analytical_overall
)
```
```{r}
not_ignored_pivot <- not_ignored_summary |>
  pivot_wider(
    id_cols = c(exp_level_random, partial_class),
    names_from = journal_type,
    values_from = c(Total, `Not Ignored`),
    names_glue = "{journal_type}_{.value}"
  ) |>
  mutate(across(everything(), ~ replace_na(.x, 0))) |>
  mutate(
    `Overall_Total` = Education_Total + Health_Total,
    `Overall_Not Ignored` = `Education_Not Ignored` + `Health_Not Ignored`
  ) |>
  ungroup()


not_ignored_pivot |>
  mutate(
    exp_level_random = factor(
      exp_level_random,
      levels = c("Overall", "Cluster", "Individual", "Mix")
    ),
    partial_class = factor(
      partial_class,
      levels = c(
        "Overall",
        "Grouped",
        "Observational Grouped",
        "Treatment Provider",
        "Observational Treatment Provider",
        "Complex",
        "Other"
      )
    )
  ) |>
  arrange(exp_level_random, partial_class) |>
  relocate(
    exp_level_random,
    partial_class,
    starts_with("Education"),
    starts_with("Health"),
    starts_with("Overall")
  ) |>
  rename(
    `Partial Nesting Classification` = partial_class,
    `Level of Randomization` = exp_level_random
  ) |>
  flextable() |>
  padding(
    i = ~ !(`Partial Nesting Classification` %in% c("Overall")),
    j = "Partial Nesting Classification",
    padding.left = 20
  ) |>
  separate_header() |>
  autofit() |>
  font(font = "Times New Roman", part = "all") |>
  border_remove() |>
  hline_bottom(part = "body") |>
  hline_top(part = "body") |>
  hline_top(part = "header")
```


Analytical Methods:

```{r}
analytical_approach_dat <- location_pn_dat |>
  group_by(exp_level_random, journal_type, analytical_partial_cluster_edit) |>
  summarise(Total = n()) |>
  mutate(
    analytical_partial_cluster_edit = ifelse(
      Total == 1 &
        analytical_partial_cluster_edit != "Fixed effects" &
        analytical_partial_cluster_edit != "Robust variance estimation" &
        analytical_partial_cluster_edit != "Random effects" &
        analytical_partial_cluster_edit != "Single",
      "Other",
      analytical_partial_cluster_edit
    )
  ) |>
  group_by(exp_level_random, journal_type, analytical_partial_cluster_edit) |>
  summarise(Total = sum(Total))


analytical_approach_total <- location_pn_dat |>
  group_by(exp_level_random, journal_type) |>
  summarise(Total = n()) |>
  mutate(analytical_partial_cluster_edit = "Overall")

analytical_approach_dat_all <- bind_rows(
  analytical_approach_dat,
  analytical_approach_total
)

unique(analytical_approach_dat_all$analytical_partial_cluster_edit)

analytical_levels <- c(
  "Overall",
  "Random effects",
  "Robust variance estimation",
  "Fixed effects",
  "Other",
  "Ignored",
  "Single"
)

analytical_approach_dat_summary <- analytical_approach_dat_all |>
  pivot_wider(
    id_cols = c(exp_level_random, analytical_partial_cluster_edit),
    values_from = Total,
    names_from = journal_type
  ) |>
  mutate(across(everything(), ~ replace_na(.x, 0))) |>
  mutate(Overall = Education + Health)

analytical_approach_dat_summary |>
  mutate(
    analytical_partial_cluster_edit = factor(
      analytical_partial_cluster_edit,
      levels = analytical_levels
    )
  ) |>
  arrange(
    exp_level_random,
    analytical_partial_cluster_edit
  ) |>
  relocate(
    exp_level_random,
    analytical_partial_cluster_edit,
    starts_with("Education"),
    starts_with("Health"),
    starts_with("Overall")
  ) |>
  rename(
    `Analytical Approach` = analytical_partial_cluster_edit,
    `Level of Randomization` = exp_level_random
  ) |>
  flextable() |>
  autofit() |>
  font(font = "Times New Roman", part = "all") |>
  padding(
    i = ~ !(`Analytical Approach` %in% c("Overall")),
    j = "Analytical Approach",
    padding.left = 20
  ) |>
  border_remove() |>
  hline_bottom(part = "body") |>
  hline_top(part = "body") |>
  hline_top(part = "header")
```

Controlling for Cluster assignment Mechanism
```{r}
account_assignment_dat <- location_pn_dat |>
  group_by(analytical_partial_cluster_edit) |>
  mutate(
    analytical_partial_cluster_edit = ifelse(
      n() == 1 &
        analytical_partial_cluster_edit != "Fixed effects" &
        analytical_partial_cluster_edit != "Robust variance estimation",
      "Other",
      analytical_partial_cluster_edit
    )
  ) |>
  filter(
    analytical_partial_cluster_edit == "Random effects" |
      analytical_partial_cluster_edit == "Robust variance estimation"
  ) |>
  group_by(partial_assign_type_edit, analytical_partial_cluster_assign) |>
  summarise(count = n()) |>
  ungroup() |>
  complete(
    partial_assign_type_edit,
    analytical_partial_cluster_assign,
    fill = list(count = 0)
  ) |>
  pivot_wider(
    names_from = analytical_partial_cluster_assign,
    names_prefix = "Account Cluster Assignment_",
    values_from = count
  )

account_assignment_dat <- account_assignment_dat |>
  summarise(across(-c(partial_assign_type_edit), sum)) |>
  mutate(partial_assign_type_edit = "Overall") |>
  bind_rows(account_assignment_dat)


account_assignment_dat |>
  relocate(partial_assign_type_edit, everything()) |>
  mutate(
    partial_assign_type_edit = factor(
      partial_assign_type_edit,
      levels = c(
        "Overall",
        "Matching",
        "Non-Random",
        "Non-Random within Blocks/Strata",
        "Randomized within Blocks/Strata",
        "Other"
      )
    )
  ) |>
  arrange(partial_assign_type_edit) |>
  rename(`Cluster Assignment Type` = partial_assign_type_edit) |>
  flextable() |>
  separate_header() |>
  padding(
    i = ~ !(`Cluster Assignment Type` %in% c("Overall")),
    j = "Cluster Assignment Type",
    padding.left = 20
  ) |>
  autofit() |>
  font(font = "Times New Roman", part = "all") |>
  border_remove() |>
  hline_bottom(part = "body") |>
  hline_top(part = "body") |>
  hline_top(part = "header")
```

## Research Question 4
4.	Does training or standardizing partial clusters result in lower chance of analytically adjusting for partial nesting? Does having diverse partial clusters result in an increased chance of analytically adjusting for partial nesting? 

```{r}
library(gtsummary)

location_pn_dat <- location_pn_dat |>
  mutate(
    not_ignore_pn = ifelse(
      analytical_partial_cluster_edit != "Ignored",
      "Yes",
      "No"
    )
  )

location_pn_dat |>
  filter(analytical_partial_cluster_edit != "Single") |>
  select(not_ignore_pn, partial_diversity, partial_standardization) |>
  tbl_summary(
    by = not_ignore_pn, # This splits the table by "No" and "Yes" for ignoring
    label = list(
      partial_diversity ~ "Reported Partial Clusters Varied in Charactersitics",
      partial_standardization ~ "Reported Partial Clusters were Trained or Standardized"
    )
  ) |>
  add_p(test = list(all_categorical() ~ "fisher.test")) %>% # Automatically calculates Fisher's Exact or Chi-sq
  add_overall() |> # Adds a column for the total N
  modify_header(label = "**Addressed Partial Nesting**") |>
  bold_labels() |>
  as_flex_table() |>
  autofit() |>
  font(font = "Times New Roman", part = "all") |>
  border_remove() |>
  hline_bottom(part = "body") |>
  hline_top(part = "body") |>
  hline_top(part = "header")
```

```{r}
#Confirming p values were calculated as expected
location_pn_dat |>
  filter(analytical_partial_cluster_edit != "Single") |>
  with(table(not_ignore_pn, partial_diversity)) |>
  fisher.test()

location_pn_dat |>
  filter(analytical_partial_cluster_edit != "Single") |>
  with(table(not_ignore_pn, partial_standardization)) |>
  fisher.test()
```

## Extra Tables


```{r}
location_pn_dat$analytical_outcome_type
```